### 2021-09-12 Submission/Paper/Paper.tex
intro and abstract done

 % use the "wcp" class option for workshop and conference
 % proceedings
 %\documentclass[gray]{jmlr} % test grayscale version
 %\documentclass[tablecaption=bottom]{jmlr}% journal article
 \documentclass[pmlr,twocolumn,10pt]{jmlr} % W&CP article

% \usepackage{geometry}
% \geometry{margins=0.1in,textwidth=7in}

 % The following packages will be automatically loaded:
 % amsmath, amssymb, natbib, graphicx, url, algorithm2e

 %\usepackage{rotating}% for sideways figures and tables
 %\usepackage{longtable}% for long tables

 % The booktabs package is used by this sample document
 % (it provides \toprule, \midrule and \bottomrule).
 % Remove the next line if you don't require it.

\usepackage{booktabs}
 % The siunitx package is used by this sample document
 % to align numbers in a column by their decimal point.
 % Remove the next line if you don't require it.
\usepackage[load-configurations=version-1]{siunitx} % newer version 
%\usepackage{siunitx}

 % The following command is just for this sample document:
\newcommand{\cs}[1]{\texttt{\char`\\#1}}% remove this in your real article

% The following is to recognise equal contribution for authorship
\newcommand{\equal}[1]{{\hypersetup{linkcolor=black}\thanks{#1}}}

 % Define an unnumbered theorem just for this sample document for
 % illustrative purposes:
\theorembodyfont{\upshape}
\theoremheaderfont{\scshape}
\theorempostheader{:}
\theoremsep{\newline}
\newtheorem*{note}{Note}

 % change the arguments, as appropriate, in the following:
\jmlrvolume{LEAVE UNSET}
\jmlryear{2021}
\jmlrsubmitted{LEAVE UNSET}
\jmlrpublished{LEAVE UNSET}
\jmlrworkshop{Machine Learning for Health (ML4H) 2021} % W&CP title

 % The optional argument of \title is used in the header
\title[Short Title]{Full Title of Article\titlebreak This Title Has
A Line Break}

 % Anything in the title that should appear in the main title but 
 % not in the article's header or the volume's table of
 % contents should be placed inside \titletag{}

 %\title{Title of the Article\titletag{\thanks{Some footnote}}}

 % Use \Name{Author Name} to specify the name.
 % If the surname contains spaces, enclose the surname
 % in braces, e.g. \Name{John {Smith Jones}} similarly
 % if the name has a "von" part, e.g \Name{Jane {de Winter}}.
 % If the first letter in the forenames is a diacritic
 % enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}

 % \thanks must come after \Name{...} not inside the argument for
 % example \Name{John Smith}\nametag{\thanks{A note}} NOT \Name{John
 % Smith\thanks{A note}}

 % Anything in the name that should appear in the title but not in the 
 % article's header or footer or in the volume's
 % table of contents should be placed inside \nametag{}

 % Two authors with the same address
 % \author{%
 %  \Name{Author Name1\nametag{\thanks{A note}}} \Email{abc@sample.com}\and
 %  \Name{Author Name2} \Email{xyz@sample.com}\\
 %  \addr Address
 % }

 % Three or more authors with the same address:
 % \author{%
 %  \Name{Author Name1} \Email{an1@sample.com}\\
 %  \Name{Author Name2} \Email{an2@sample.com}\\
 %  \Name{Author Name3} \Email{an3@sample.com}\\
 %  \Name{Author Name4} \Email{an4@sample.com}\\
 %  \Name{Author Name5} \Email{an5@sample.com}\\
 %  \Name{Author Name6} \Email{an6@sample.com}\\
 %  \Name{Author Name7} \Email{an7@sample.com}\\
 %  \Name{Author Name8} \Email{an8@sample.com}\\
 %  \Name{Author Name9} \Email{an9@sample.com}\\
 %  \Name{Author Name10} \Email{an10@sample.com}\\
 %  \Name{Author Name11} \Email{an11@sample.com}\\
 %  \Name{Author Name12} \Email{an12@sample.com}\\
 %  \Name{Author Name13} \Email{an13@sample.com}\\
 %  \Name{Author Name14} \Email{an14@sample.com}\\
 %  \addr Address
 % }

 % Authors with different addresses and equal first authors:
\author{%
\Name{First Author 1}\equal{These authors contributed equally} \Email{abc@sample.com}\\
\addr University X, Country 1
\AND
% footnotemark[1] is to refer to the \equal footnote
\Name{First Author 2}\footnotemark[1] \Email{def@sample.com}\\
\addr University Y, Country 2
\AND
\Name{Last Author} \Email{ghi@sample.com}\\
\addr University Z, Country 3
}

\begin{document}

\maketitle

\begin{abstract}
Parkinson’s disease (PD) is debilitating, progressive, and clinically marked by motor symptoms, which affects over 10 million lives around the world. As the second most common neurodegenerative disease with no approved treatments, the existing diagnosis methods have limitations, such as the expense of visiting doctors and the challenge of automated early detection, considering that symptoms and behavioral differences in patients and healthy individuals are often not present in early stages. Micrographia is a disorder commonly observed in early stages of PD. In order to establish mechanisms for early detection of PD, we applied machine and deep learning techniques to extract signs of micrographia from drawing samples gathered from a variety of open-source datasets. We have discovered that a Convolutional Neural Network (CNN) performs best and can reliably learn important information solely from raw images. This work sets the foundations for a web portal allowing any individual worldwide with access to a pen, printer, and phone to upload an image of a handwriting assessment we designed and receive a PD diagnosis in real-time.
\end{abstract}
\begin{keywords}
CNN, Parkinson’s, PD, micrographia, disorder, early detection, diagnosis, neurodegenerative
\end{keywords}

\section{Introduction}
\label{sec:intro}

Parkinson’s disease (PD) is a degenerative, chronic, and progressive nervous system disorder that affects movement. More than 10 million people worldwide are currently living with PD, and the number of cases is expected to more than double in the next decade. Symptoms include tremors, slowness of movement, stiffness, and changes in writing skills. PD occurs when dopamine-producing nerve cells die, a process that can take almost 10 years to reach its late and most severe stages. A lack of dopamine results in further critical symptoms, such as depression, anxiety, sleep disturbances, and dementia.

Parkinson’s disease cannot be treated, although specific drugs and medications can assist with symptoms in early stages, potentially preventing the disease’s progression to more severe stages. Early detection and prognosis of PD are crucial for assisting patients to retain a good quality of life. However, diagnosing Parkinson’s disease in its early stages is a very challenging task, and there are currently no specific tests designed to diagnose PD. Diagnosis is based on a thorough examination performed by a trained medical official, including a neurological examination, medical history evaluation, blood and laboratory tests, and brain scans. Even with these procedures, PD is misdiagnosed up to 30\% of the time, especially in early stages, due to the many Parkinson’s mimics, the main ones being Essential Tremors and Drug Induced Parkinson’s. Additionally, up to 20\% of PD patients are undiagnosed. Receiving a PD diagnosis is expensive, time consuming, and non-accessible, as reported by 21\% of patients who had to visit their general provider thrice before receiving a specialist referral for their condition.

Tools that can make the diagnosis process accurate, accessible, automatic, real-time, early, and free of cost can have tremendous impact for Parkinson’s patients. In this study, we apply machine and deep learning strategies on a variety of data, including both image and numerical features. We present a Convolutional Neural Network model able to uncover signs of Parkinson’s in drawing images and compare it to machine learning models.

\begin{note}
This is an numbered theorem-like environment that was defined in
this document's preamble.
\end{note}

\subsection{Sub-sections}

Sub-sections are produced using \verb|\subsection|.

\subsubsection{Sub-sub-sections}

Sub-sub-sections are produced using \verb|\subsubsection|.

\paragraph{Sub-sub-sub-sections}

Sub-sub-sub-sections are produced using \verb|\paragraph|.
These are unnumbered with a running head.

\subparagraph{Sub-sub-sub-sub-sections}

Sub-sub-sub-sub-sections are produced using \verb|\subparagraph|.
These are unnumbered with a running head.

\section{Cross-Referencing}

Always use \verb|\label| and \verb|\ref| (or one of the commands
described below) when cross-referencing.  For example, the next
section is Section~\ref{sec:math} but you can also refer to it using
\sectionref{sec:math}. The \textsf{jmlr} class
provides some convenient cross-referencing commands:
\verb|\sectionref|, \verb|\equationref|, \verb|\tableref|,
\verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|,
\verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|,
\verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|,
\verb|\exampleref| and \verb|\appendixref|. The argument of these
commands may either be a single label or a comma-separated list
of labels. Examples:

Referencing sections: \sectionref{sec:math} or
\sectionref{sec:intro,sec:math} or
\sectionref{sec:intro,sec:math,sec:tables,sec:figures}.

Referencing equations: \equationref{eq:trigrule} or
\equationref{eq:trigrule,eq:df} or
\equationref{eq:trigrule,eq:f,eq:df,eq:y}.

Referencing tables: \tableref{tab:operatornames} or
\tableref{tab:operatornames,tab:example} or
\tableref{tab:operatornames,tab:example,tab:example-booktabs}.

Referencing figures: \figureref{fig:nodes} or
\figureref{fig:nodes,fig:teximage} or
\figureref{fig:nodes,fig:teximage,fig:subfigex} or
\figureref{fig:circle,fig:square}.

Referencing algorithms: \algorithmref{alg:gauss} or
\algorithmref{alg:gauss,alg:moore} or
\algorithmref{alg:gauss,alg:moore,alg:net}.

Referencing theorem-like environments: \theoremref{thm:eigenpow},
\lemmaref{lem:sample}, \remarkref{rem:sample}, 
\corollaryref{cor:sample}, \definitionref{def:sample},
\conjectureref{con:sample}, \axiomref{ax:sample} and
\exampleref{ex:sample}.

Referencing appendices: \appendixref{apd:first} or
\appendixref{apd:first,apd:second}.

\section{Equations}
\label{sec:math}

The \textsf{jmlr} class loads the \textsf{amsmath} package, so
you can use any of the commands and environments defined there.
(See the \textsf{amsmath} documentation for further
details.\footnote{Either \texttt{texdoc amsmath} or
\url{http://www.ctan.org/pkg/amsmath}})

Unnumbered single-lined equations should be displayed using
\verb|\[| and \verb|\]|. For example:
\[E = m c^2\]
or you can use the \texttt{displaymath} environment:
\begin{displaymath}
E = m c^2
\end{displaymath}
Numbered single-line equations should be displayed using the
\texttt{equation} environment. For example:
\begin{equation}\label{eq:trigrule}
\cos^2\theta + \sin^2\theta \equiv 1
\end{equation}
This can be referenced using \verb|\label| and \verb|\equationref|.
For example, \equationref{eq:trigrule}.

Multi-lined numbered equations should be displayed using the
\texttt{align} environment.\footnote{For reasons why you 
shouldn't use the obsolete \texttt{eqnarray} environment, see
Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
\begin{align}
f(x) &= x^2 + x\label{eq:f}\\
f'(x) &= 2x + 1\label{eq:df}
\end{align}
Unnumbered multi-lined equations can be displayed using the
\texttt{align*} environment. For example:
\begin{align*}
f(x) &= (x+1)(x-1)\\
&= x^2 - 1
\end{align*}
If you want to mix numbered with unnumbered lines use the
\texttt{align} environment and suppress unwanted line numbers with
\verb|\nonumber|. For example:
\begin{align}
y &= x^2 + 3x - 2x + 1\nonumber\\
&= x^2 + x + 1\label{eq:y}
\end{align}
An equation that is too long to fit on a single line can be
displayed using the \texttt{split} environment. 
Text can be embedded in an equation using \verb|\text| or
\verb|\intertext| (as used in \theoremref{thm:eigenpow}).
See the \textsf{amsmath} documentation for further details.

\subsection{Operator Names}
\label{sec:op}

Predefined operator names are listed in \tableref{tab:operatornames}.
For additional operators, either use \verb|\operatorname|,
for example $\operatorname{var}(X)$ or declare it with
\verb|\DeclareMathOperator|, for example
\begin{verbatim}
\DeclareMathOperator{\var}{var}
\end{verbatim}
and then use this new command. If you want limits that go above and
below the operator (like \verb|\sum|) use the starred versions
(\verb|\operatorname*| or \verb|\DeclareMathOperator*|).

\begin{table*}[htbp]
\floatconts
  {tab:operatornames}%
  {\caption{Predefined Operator Names (taken from 
   \textsf{amsmath} documentation)}}%
  {%
\begin{tabular}{rlrlrlrl}
\cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
\cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
\cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
\cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
\cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
\cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
\cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
\cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
\cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
\end{tabular}\par
\begin{tabular}{rlrl}
\cs{varlimsup} & $\varlimsup$ 
& \cs{varinjlim} & $\varinjlim$\\
\cs{varliminf} & $\varliminf$ 
& \cs{varprojlim} & $\varprojlim$
\end{tabular}
}
\end{table*}

\section{Vectors and Sets}
\label{sec:vec}

Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
(The original version of \cs{vec} can also be accessed using
\cs{orgvec}, for example $\orgvec{x}$.)
The \textsf{jmlr} class also provides \cs{set} to typeset a
set. For example $\set{S}$.

\section{Floats}
\label{sec:floats}

Floats, such as figures, tables and algorithms, are moving
objects and are supposed to float to the nearest convenient
location. Please don't force them to go in a particular place. In
general it's best to use the \texttt{htbp} specifier and don't
put the figure or table in the middle of a paragraph (that is
make sure there's a paragraph break above and below the float).
Floats are supposed to have a little extra space above and below
them to make them stand out from the rest of the text. This extra
spacing is put in automatically and shouldn't need modifying.

If your article will later be reprinted in the Challenges for
Machine Learning, please be aware that the CiML books use a
different paper size, so if you want to resize any images use a
scale relative to the line width (\verb|\linewidth|), text width
(\verb|\textwidth|) or text height (\verb|\textheight|).

To ensure consistency, please \emph{don't} try changing the format of the caption by doing
something like:
\begin{verbatim}
\caption{\textit{A Sample Caption.}}
\end{verbatim}
or
\begin{verbatim}
\caption{\em A Sample Caption.}
\end{verbatim}
You can, of course, change the font for individual words or 
phrases, for example:
\begin{verbatim}
\caption{A Sample Caption With Some \emph{Emphasized Words}.}
\end{verbatim}

\subsection{Tables}
\label{sec:tables}

Tables should go in the \texttt{table} environment. Within this
environment use \verb|\floatconts| (defined by \textsf{jmlr})
to set the caption correctly and center the table contents.
The location of the caption depends on the \verb|tablecaption|
setting in the document class options.

\begin{table}[htbp]
 % The first argument is the label.
 % The caption goes in the second argument, and the table contents
 % go in the third argument.
\floatconts
  {tab:example}%
  {\caption{An Example Table}}%
  {\begin{tabular}{ll}
  \bfseries Dataset & \bfseries Result\\
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876
  \end{tabular}}
\end{table}

If you want horizontal rules you can use the \textsf{booktabs}
package which provides the commands \verb|\toprule|, 
\verb|\midrule| and \verb|\bottomrule|. For example, see
\tableref{tab:example-booktabs}.

\begin{table}[hbtp]
\floatconts
  {tab:example-booktabs}
  {\caption{A Table With Horizontal Lines}}
  {\begin{tabular}{ll}
  \toprule
  \bfseries Dataset & \bfseries Result\\
  \midrule
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876\\
  \bottomrule
  \end{tabular}}
\end{table}

If you really want vertical lines as well, you can't use the
\textsf{booktabs} commands as there'll be some unwanted gaps.
Instead you can use \LaTeX's \verb|\hline|, but the rows may
appear a bit cramped.  You can add extra space above or below a
row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
see \tableref{tab:example-hline}. However, you might want to read
the \textsf{booktabs} documentation regarding the use of vertical
lines.

\begin{table}[htbp]
\floatconts
  {tab:example-hline}
  {\caption{A Table With Horizontal and Vertical Lines}}%
  {%
    \begin{tabular}{|l|l|}
    \hline
    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
    \abovestrut{2.2ex}Data1 & 0.12345\\
    Data2 & 0.67890\\
    Data3 & 0.54321\\
    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
    \end{tabular}
  }
\end{table}

If you want to align numbers on their decimal point, you can
use the \textsf{siunitx} package. For example, see
\tableref{tab:example-siunitx}. For further details see the
\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.

\begin{table}[htbp]
\floatconts
  {tab:example-siunitx}
  {\caption{A Table With Numbers Aligned on the Decimal Point}}
  {\begin{tabular}{lS[tabformat=3.5]}
  \bfseries Dataset & {\bfseries Result}\\
  Data1 & 0.12345\\
  Data2 & 10.6789\\
  Data3 & 50.543\\
  Data4 & 200.09876
  \end{tabular}}
\end{table}

If the table is too wide, you can adjust the inter-column
spacing by changing the value of \verb|\tabcolsep|. For
example:
\begin{verbatim}
\setlength{\tabcolsep}{3pt}
\end{verbatim}
If the table is very wide but not very long, you can use the
\texttt{sidewaystable} environment defined in the
\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
If the table is too long to fit on a page, you can use the
\texttt{longtable} environment defined in the \textsf{longtable}
package (so use \verb|\usepackage{longtable}|).

\subsection{Figures}
\label{sec:figures}

Figures should go in the \texttt{figure} environment. Within this
environment, use \verb|\floatconts| to correctly position the
caption and center the image. Use \verb|\includegraphics|
for external graphics files but omit the file extension. Do not
use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
image, it's better to use a fraction of the line width rather
than an explicit length. For example, see \figureref{fig:nodes}.

\begin{figure}[htbp]
 % Caption and label go in the first argument and the figure contents
 % go in the second argument
\floatconts
  {fig:nodes}
  {\caption{Example Image}}
  {\includegraphics[width=0.5\linewidth]{images/nodes}}
\end{figure}

If your image is made up of \LaTeX\ code (for example, commands
provided by the \textsf{pgf} package) you can include it using
\cs{includeteximage} (defined by the \textsf{jmlr} class). This
can be scaled and rotated in the same way as \cs{includegraphics}.
For example, see \figureref{fig:teximage}.

\begin{figure}[htbp]
\floatconts
  {fig:teximage}
  {\caption{Image Created Using \LaTeX\ Code}}
  {\includeteximage[angle=45]{images/teximage}}
\end{figure}

If the figure is too wide to fit on the page, you can use the
\texttt{sidewaysfigure} environment defined in the
\textsf{rotating} package.

Don't use \verb|\graphicspath|.\footnote{This is specific to the
\textsf{jmlr} class, not a general recommendation. The main file
that generates the proceedings or the CiML book is typically in a
different directory to the imported articles, so it modifies the
graphics path when it imports an article.} If the images 
are contained in a subdirectory, specify this when you include the image, for
example \verb|\includegraphics{figures/mypic}|.

\subsubsection{Sub-Figures}
\label{sec:subfigures}

Sub-figures can be created using \verb|\subfigure|, which is
defined by the \textsf{jmlr} class. The optional argument allows
you to provide a subcaption. The label should be placed in the
mandatory argument of \verb|\subfigure|. You can reference the
entire figure, for example \figureref{fig:subfigex}, or you can
reference part of the figure using \verb|\figureref|, for example
\figureref{fig:circle}. Alternatively you can reference the
subfigure using \verb|\subfigref|, for example
\subfigref{fig:circle,fig:square} in \figureref{fig:subfigex}.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex}
  {\caption{An Example With Sub-Figures.}}
  {%
    \subfigure[A Circle]{\label{fig:circle}%
      \includegraphics[width=0.2\linewidth]{images/circle}}%
    \qquad
    \subfigure[A Square]{\label{fig:square}%
      \includegraphics[width=0.2\linewidth]{images/square}}
  }
\end{figure}

By default, the sub-figures are aligned on the baseline.
This can be changed using the second optional argument
of \verb|\subfigure|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the subfigures
\subfigref{fig:circle2,fig:square2} in \figureref{fig:subfigex2}
both have \verb|[c]| as the second optional argument.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex2}
  {\caption{Another Example With Sub-Figures.}}
  {%
    \subfigure[A Small Circle][c]{\label{fig:circle2}%
      \includegraphics[width=0.1\linewidth]{images/circle}}%
    \qquad
    \subfigure[A Square][c]{\label{fig:square2}%
      \includegraphics[width=0.2\linewidth]{images/square}}
  }
\end{figure}

\subsection{Sub-Tables}
\label{sec:subtables}
There is an analogous command \verb|\subtable| for sub-tables.
It has the same syntax as \verb|\subfigure| described above.
You can reference the table using \verb|\tableref|, for example
\tableref{tab:subtabex} or you can reference part of the table,
for example \tableref{tab:ab}. Alternatively you can reference the
subtable using \verb|\subtabref|, for example
\subtabref{tab:ab,tab:cd} in \tableref{tab:subtabex}.

\begin{table}[htbp]
\floatconts
 {tab:subtabex}
 {\caption{An Example With Sub-Tables}}
 {%
   \subtable{%
     \label{tab:ab}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable{%
     \label{tab:cd}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

By default, the sub-tables are aligned on the top.
This can be changed using the second optional argument
of \verb|\subtable|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the sub-tables
\subtabref{tab:ab2,tab:cd2} in \tableref{tab:subtabex2}
both have \verb|[c]| as the second optional argument.

\begin{table}[htbp]
\floatconts
 {tab:subtabex2}
 {\caption{Another Example With Sub-Tables}}
 {%
   \subtable[][c]{%
     \label{tab:ab2}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable[][c]{%
     \label{tab:cd2}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

\subsection{Algorithms}
\label{sec:algorithms}

Enumerated textual algorithms can be displayed using the
\texttt{algorithm} environment. Within this environment, use
\verb|\caption| to set the caption and you can use an
\texttt{enumerate} or nested \texttt{enumerate} environments.
For example, see \algorithmref{alg:gauss}. Note that algorithms
float like figures and tables.

\begin{algorithm}[htbp]
\floatconts
  {alg:gauss}%
  {\caption{The Gauss-Seidel Algorithm}}%
{%
\begin{enumerate}
  \item For $k=1$ to maximum number of iterations
    \begin{enumerate}
      \item For $i=1$ to $n$
        \begin{enumerate}
        \item $x_i^{(k)} = 
          \frac{b_i - \sum_{j=1}^{i-1}a_{ij}x_j^{(k)}
          - \sum_{j=i+1}^{n}a_{ij}x_j^{(k-1)}}{a_{ii}}$
        \item If $\|\vec{x}^{(k)}-\vec{x}^{(k-1)} < \epsilon\|$,
          where $\epsilon$ is a specified stopping criteria, stop.
      \end{enumerate}
    \end{enumerate}
\end{enumerate}
}%
\end{algorithm}

If you'd rather have the same numbering throughout the algorithm
but still want the convenient indentation of nested 
\texttt{enumerate} environments, you can use the
\texttt{enumerate*} environment provided by the \textsf{jmlr}
class. For example, see \algorithmref{alg:moore}.

\begin{algorithm}
\floatconts
  {alg:moore}%
  {\caption{Moore's Shortest Path}}%
{%
Given a connected graph $G$, where the length of each edge is 1:
\begin{enumerate*}
  \item Set the label of vertex $s$ to 0
  \item Set $i=0$
  \begin{enumerate*}
    \item \label{step:locate}Locate all unlabelled vertices 
          adjacent to a vertex labelled $i$ and label them $i+1$
    \item If vertex $t$ has been labelled,
    \begin{enumerate*}
      \item[] the shortest path can be found by backtracking, and 
      the length is given by the label of $t$.
    \end{enumerate*}
    otherwise
    \begin{enumerate*}
      \item[] increment $i$ and return to step~\ref{step:locate}
    \end{enumerate*}
  \end{enumerate*}
\end{enumerate*}
}%
\end{algorithm}

Pseudo code can be displayed using the \texttt{algorithm2e}
environment. This is defined by the \textsf{algorithm2e} package
(which is automatically loaded) so check the \textsf{algorithm2e}
documentation for further details.\footnote{Either \texttt{texdoc
algorithm2e} or \url{http://www.ctan.org/pkg/algorithm2e}}
For an example, see \algorithmref{alg:net}.

\begin{algorithm2e}
\caption{Computing Net Activation}
\label{alg:net}
 % older versions of algorithm2e have \dontprintsemicolon instead
 % of the following:
 %\DontPrintSemicolon
 % older versions of algorithm2e have \linesnumbered instead of the
 % following:
 %\LinesNumbered
\KwIn{$x_1, \ldots, x_n, w_1, \ldots, w_n$}
\KwOut{$y$, the net activation}
$y\leftarrow 0$\;
\For{$i\leftarrow 1$ \KwTo $n$}{
  $y \leftarrow y + w_i*x_i$\;
}
\end{algorithm2e}

\section{Description Lists}

The \textsf{jmlr} class also provides a description-like 
environment called \texttt{altdescription}. This has an
argument that should be the widest label in the list. Compare:
\begin{description}
\item[add] A method that adds two variables.
\item[differentiate] A method that differentiates a function.
\end{description}
with
\begin{altdescription}{differentiate}
\item[add] A method that adds two variables.
\item[differentiate] A method that differentiates a function.
\end{altdescription}

\section{Theorems, Lemmas etc}
\label{sec:theorems}

The following theorem-like environments are predefined by
the \textsf{jmlr} class: \texttt{theorem}, \texttt{example},
\texttt{lemma}, \texttt{proposition}, \texttt{remark}, 
\texttt{corollary}, \texttt{definition}, \texttt{conjecture}
and \texttt{axiom}. You can use the \texttt{proof} environment
to display the proof if need be, as in \theoremref{thm:eigenpow}.

\begin{theorem}[Eigenvalue Powers]\label{thm:eigenpow}
If $\lambda$ is an eigenvalue of $\vec{B}$ with eigenvector
$\vec{\xi}$, then $\lambda^n$ is an eigenvalue of $\vec{B}^n$
with eigenvector $\vec{\xi}$.
\begin{proof}
Let $\lambda$ be an eigenvalue of $\vec{B}$ with eigenvector
$\xi$, then
\begin{align*}
\vec{B}\vec{\xi} &= \lambda\vec{\xi}
\intertext{premultiply by $\vec{B}$:}
\vec{B}\vec{B}\vec{\xi} &= \vec{B}\lambda\vec{\xi}\\
\Rightarrow \vec{B}^2\vec{\xi} &= \lambda\vec{B}\vec{\xi}\\
&= \lambda\lambda\vec{\xi}\qquad
\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
&= \lambda^2\vec{\xi}
\end{align*}
Therefore true for $n=2$. Now assume true for $n=k$:
\begin{align*}
\vec{B}^k\vec{\xi} &= \lambda^k\vec{\xi}
\intertext{premultiply by $\vec{B}$:}
\vec{B}\vec{B}^k\vec{\xi} &= \vec{B}\lambda^k\vec{\xi}\\
\Rightarrow \vec{B}^{k+1}\vec{\xi} &= \lambda^k\vec{B}\vec{\xi}\\
&= \lambda^k\lambda\vec{\xi}\qquad
\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
&= \lambda^{k+1}\vec{\xi}
\end{align*}
Therefore true for $n=k+1$. Therefore, by induction, true for all
$n$.
\end{proof}
\end{theorem}

\begin{lemma}[A Sample Lemma]\label{lem:sample}
This is a lemma.
\end{lemma}

\begin{remark}[A Sample Remark]\label{rem:sample}
This is a remark.
\end{remark}

\begin{corollary}[A Sample Corollary]\label{cor:sample}
This is a corollary.
\end{corollary}

\begin{definition}[A Sample Definition]\label{def:sample}
This is a definition.
\end{definition}

\begin{conjecture}[A Sample Conjecture]\label{con:sample}
This is a conjecture.
\end{conjecture}

\begin{axiom}[A Sample Axiom]\label{ax:sample}
This is an axiom.
\end{axiom}

\begin{example}[An Example]\label{ex:sample}
This is an example.
\end{example}

\section{Color vs Grayscale}
\label{sec:color}

It's helpful if authors supply grayscale versions of their
images in the event that the article is to be incorporated into
a black and white printed book. With external PDF, PNG or JPG
graphic files, you just need to supply a grayscale version of the
file. For example, if the file is called \texttt{myimage.png},
then the gray version should be \texttt{myimage-gray.png} or
\texttt{myimage-gray.pdf} or \texttt{myimage-gray.jpg}. You don't
need to modify your code. The \textsf{jmlr} class checks for
the existence of the grayscale version if it is print mode 
(provided you have used \verb|\includegraphics| and haven't
specified the file extension).

You can use \verb|\ifprint| to determine which mode you are in.
For example, in \figureref{fig:nodes}, the 
\ifprint{dark gray}{purple} ellipse represents an input and the
\ifprint{light gray}{yellow} ellipse represents an output.
Another example: {\ifprint{\bfseries}{\color{red}}important text!}

You can use the class option \texttt{gray} to see how the
document will appear in gray scale mode. \textcolor{blue}{Colored
text} will automatically be converted to gray scale in print mode.

The \textsf{jmlr} class loads the \textsf{xcolor}
package, so you can also define your own colors. For example:
\ifprint
  {\definecolor{myred}{gray}{0.5}}%
  {\definecolor{myred}{rgb}{0.5,0,0}}%
\textcolor{myred}{XYZ}.

The \textsf{xcolor} class is loaded with the \texttt{x11names}
option, so you can use any of the x11 predefined colors (listed
in the \textsf{xcolor} documentation\footnote{either 
\texttt{texdoc xcolor} or \url{http://www.ctan.org/pkg/xcolor}}).

\section{Citations and Bibliography}
\label{sec:cite}

The \textsf{jmlr} class automatically loads \textsf{natbib}
and automatically sets the bibliography style, so you don't need to
use \verb|\bibliographystyle|.
This sample file has the citations defined in the accompanying
BibTeX file \texttt{jmlr-sample.bib}. For a parenthetical
citation use \verb|\citep|. For example
\citep{guyon-elisseeff-03}. For a textual citation use
\verb|\citet|. For example \citet{guyon2007causalreport}. 
Both commands may take a comma-separated list, for example
\citet{guyon-elisseeff-03,guyon2007causalreport}.

These commands have optional arguments and have a starred
version. See the \textsf{natbib} documentation for further
details.\footnote{Either \texttt{texdoc natbib} or
\url{http://www.ctan.org/pkg/natbib}}

The bibliography is displayed using \verb|\bibliography|.

\acks{Acknowledgements go here.}

\bibliography{jmlr-sample}

\appendix

\section{First Appendix}\label{apd:first}

This is the first appendix.

\section{Second Appendix}\label{apd:second}

This is the second appendix.

\end{document}

### 2021-09-12 Submission/Paper/Paper.tex
finished math formulas

@@
  \documentclass[pmlr,twocolumn,10pt]{jmlr} % W&CP article
+
+ \let\SUP\textsuperscript
 
@@
 
- % Anything in the title that should appear in the main title but 
- % not in the article's header or the volume's table of
- % contents should be placed inside \titletag{}
-
- %\title{Title of the Article\titletag{\thanks{Some footnote}}}
-
- % Use \Name{Author Name} to specify the name.
- % If the surname contains spaces, enclose the surname
- % in braces, e.g. \Name{John {Smith Jones}} similarly
- % if the name has a "von" part, e.g \Name{Jane {de Winter}}.
- % If the first letter in the forenames is a diacritic
- % enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}
-
- % \thanks must come after \Name{...} not inside the argument for
- % example \Name{John Smith}\nametag{\thanks{A note}} NOT \Name{John
- % Smith\thanks{A note}}
-
- % Anything in the name that should appear in the title but not in the 
- % article's header or footer or in the volume's
- % table of contents should be placed inside \nametag{}
-
- % Two authors with the same address
- % \author{%
- %  \Name{Author Name1\nametag{\thanks{A note}}} \Email{abc@sample.com}\and
- %  \Name{Author Name2} \Email{xyz@sample.com}\\
- %  \addr Address
- % }
-
- % Three or more authors with the same address:
- % \author{%
- %  \Name{Author Name1} \Email{an1@sample.com}\\
- %  \Name{Author Name2} \Email{an2@sample.com}\\
- %  \Name{Author Name3} \Email{an3@sample.com}\\
- %  \Name{Author Name4} \Email{an4@sample.com}\\
- %  \Name{Author Name5} \Email{an5@sample.com}\\
- %  \Name{Author Name6} \Email{an6@sample.com}\\
- %  \Name{Author Name7} \Email{an7@sample.com}\\
- %  \Name{Author Name8} \Email{an8@sample.com}\\
- %  \Name{Author Name9} \Email{an9@sample.com}\\
- %  \Name{Author Name10} \Email{an10@sample.com}\\
- %  \Name{Author Name11} \Email{an11@sample.com}\\
- %  \Name{Author Name12} \Email{an12@sample.com}\\
- %  \Name{Author Name13} \Email{an13@sample.com}\\
- %  \Name{Author Name14} \Email{an14@sample.com}\\
- %  \addr Address
- % }
-
  % Authors with different addresses and equal first authors:
-\author{%
-\Name{First Author 1}\equal{These authors contributed equally} \Email{abc@sample.com}\\
-\addr University X, Country 1
-\AND
-% footnotemark[1] is to refer to the \equal footnote
-\Name{First Author 2}\footnotemark[1] \Email{def@sample.com}\\
-\addr University Y, Country 2
-\AND
-\Name{Last Author} \Email{ghi@sample.com}\\
-\addr University Z, Country 3
+\author{Riya Tyagi \nametag{\thanks{Authors contributed equally}\SUP{1}},
+Tanish Tyagi \nametag{\footnotemark[1]\SUP{2}}, 
+Ming Wang \SUP{3},
+Lijun Zhang \SUP{4},
+\centering \Email{
+\\[\bigskipamount] 
+\SUP{1}\{rtyagi\}
+@exeter.edu}
+\centering \Email{
+\\[\bigskipamount] 
+\SUP{2}\{ttyagi\}@mgh.harvard.edu}
+\centering \Email{
+\\[\bigskipamount] 
+\SUP{3}\{mwang\}@phs.psu.edu}
+\centering \Email{
+\\[\bigskipamount] 
+\SUP{4}\{lzhang6\}@pennstatehealth.psu.edu}
 }
@@
 
-\begin{note}
-This is an numbered theorem-like environment that was defined in
-this document's preamble.
-\end{note}
+\section{Related Works}
+\label{related-works}
+Prior works have incorporated the use of voice recordings, electroencephalogram (EEG) signals, and smart devices to create models that deduce whether a patient has PD or not.
+Zhao et al.
+hypothesized that patients with PD exhibit deficits in the production of emotional speech.
+To test this conjecture, five patients and seven healthy individuals were used to recognize Parkinson’s disease through voice recordings.
+Naive Bayes, Random Forests, and Support Vector Machines were applied for classification, achieving 65.5\% and 73.33\% accuracies on classifying PD and control.
+Oh et al.
+utilized EEG signals and a Convolutional Neural Network (CNN) to detect PD
+by assessing whether the EEG signals depicted brain abnormalities, achieving 88.25\% accuracy.
+Drotár et al.
+employed the use of a digitizing tablet to assess both in-air and on-surface kinematic variables during handwriting of a sentence in 37 PD patients on medication and 38 age- and gender-matched healthy controls.
+Using Support Vector Machines, an accuracy of 85.61\% was achieved.
+These studies require patients to visit a neurologist to access a smart device and undergo various scans like EEG and PET, making the process expensive, time-consuming, and difficult to access.
+In this study, we aim to make the PD diagnosis process accurate, efficient, and accessible by using images of handwriting samples to automate the PD diagnosis process.
 
-\subsection{Sub-sections}
+\section{Dataset and Preprocessing}
+\label{sec:Dataset+Preprocessing}
 
-Sub-sections are produced using \verb|\subsection|.
+\paragraph{Dataset}
+\label{sec:Dataset} Our dataset was formed by combining the New HandPD and Old HandPD dataset available at (https://wwwp.fc.unesp.br/~papa/pub/datasets/Handpd/).
+It consists of 158 individuals, 53 healthy and 105 PD patients.
+Each patient drew 8 images, 4 spirals and 4 meander.
+With these images, we constructed 2 datasets, one consisting of extracted numerical features and the other consisting of images.
 
-\subsubsection{Sub-sub-sections}
+\paragraph{Preprocessing}
+\label{sec:Preprocessing} 
+We mimicked the feature extraction process used (cite handpd ppl) to extract 9 numerical features from the images.
+First, the handwritten trace (HT) and exam trace (ET) were extracted from the image.
+Figure (X) shows an example image and the extracted HT and ET.
+Using the HT and ET, the below features were computed:
 
-Sub-sub-sections are produced using \verb|\subsubsection|.
+\begin{enumerate}
+\item The root mean square (RMS) of the differences between the HT and ET radii.
+The radius of the HT or ET can be defined as the length of the straight line that connects an arbitrary point to the center of the HT or ET and is shown in figure (X).
+$N$ is the number of sample points on the HT and ET.
+\[RMS = \sqrt{\frac{1}{N} * \sum_\SUP{i=1}^N(r_\SUP{HT}^i - r_\SUP{ET}^i)^2}\]
 
-\paragraph{Sub-sub-sub-sections}
+\item The maximum difference between the HT and ET radii. 
+\[\Delta max = max(|r_\SUP{HT}^i - r_\SUP{ET}^i|)\]
 
-Sub-sub-sub-sections are produced using \verb|\paragraph|.
-These are unnumbered with a running head.
+\item F3: The minimum difference between the HT and ET radii. 
+\[\Delta min = min(|r_\SUP{HT}^i - r_\SUP{ET}^i|)\]
 
-\subparagraph{Sub-sub-sub-sub-sections}
+\item F4: The standard deviation of the differences between the HT and ET radii. 
+\[s = \sqrt{\frac{1}{N-1}\sum_{i=1}^N(r_\SUP{HT}^i - r_\SUP{ET}^i)^2}\]
 
-Sub-sub-sub-sub-sections are produced using \verb|\subparagraph|.
-These are unnumbered with a running head.
+\item F5: The Mean Relative Tremor (mrt) of a given individual’s HT.
+This is defined as the mean difference between the radius of a given sample and its D left-nearest neighbors.
+To find D, D = {1, 3, 5, 7, 10, 15, 20} were tested, with D = 10 maximizing the PD detection rate.
+\[MRT = \frac{1}{N-D}\sum_\SUP{i=D}^N(|r_\SUP{HT}^\SUP{i-D+1} - r_\SUP{ET}^i|)\]
 
-\section{Cross-Referencing}
-
-Always use \verb|\label| and \verb|\ref| (or one of the commands
-described below) when cross-referencing.  For example, the next
-section is Section~\ref{sec:math} but you can also refer to it using
-\sectionref{sec:math}. The \textsf{jmlr} class
-provides some convenient cross-referencing commands:
-\verb|\sectionref|, \verb|\equationref|, \verb|\tableref|,
-\verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|,
-\verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|,
-\verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|,
-\verb|\exampleref| and \verb|\appendixref|. The argument of these
-commands may either be a single label or a comma-separated list
-of labels. Examples:
-
-Referencing sections: \sectionref{sec:math} or
-\sectionref{sec:intro,sec:math} or
-\sectionref{sec:intro,sec:math,sec:tables,sec:figures}.
-
-Referencing equations: \equationref{eq:trigrule} or
-\equationref{eq:trigrule,eq:df} or
-\equationref{eq:trigrule,eq:f,eq:df,eq:y}.
-
-Referencing tables: \tableref{tab:operatornames} or
-\tableref{tab:operatornames,tab:example} or
-\tableref{tab:operatornames,tab:example,tab:example-booktabs}.
-
-Referencing figures: \figureref{fig:nodes} or
-\figureref{fig:nodes,fig:teximage} or
-\figureref{fig:nodes,fig:teximage,fig:subfigex} or
-\figureref{fig:circle,fig:square}.
-
-Referencing algorithms: \algorithmref{alg:gauss} or
-\algorithmref{alg:gauss,alg:moore} or
-\algorithmref{alg:gauss,alg:moore,alg:net}.
-
-Referencing theorem-like environments: \theoremref{thm:eigenpow},
-\lemmaref{lem:sample}, \remarkref{rem:sample}, 
-\corollaryref{cor:sample}, \definitionref{def:sample},
-\conjectureref{con:sample}, \axiomref{ax:sample} and
-\exampleref{ex:sample}.
-
-Referencing appendices: \appendixref{apd:first} or
-\appendixref{apd:first,apd:second}.
-
-\section{Equations}
-\label{sec:math}
-
-The \textsf{jmlr} class loads the \textsf{amsmath} package, so
-you can use any of the commands and environments defined there.
-(See the \textsf{amsmath} documentation for further
-details.\footnote{Either \texttt{texdoc amsmath} or
-\url{http://www.ctan.org/pkg/amsmath}})
-
-Unnumbered single-lined equations should be displayed using
-\verb|\[| and \verb|\]|. For example:
-\[E = m c^2\]
-or you can use the \texttt{displaymath} environment:
-\begin{displaymath}
-E = m c^2
-\end{displaymath}
-Numbered single-line equations should be displayed using the
-\texttt{equation} environment. For example:
-\begin{equation}\label{eq:trigrule}
-\cos^2\theta + \sin^2\theta \equiv 1
-\end{equation}
-This can be referenced using \verb|\label| and \verb|\equationref|.
-For example, \equationref{eq:trigrule}.
-
-Multi-lined numbered equations should be displayed using the
-\texttt{align} environment.\footnote{For reasons why you 
-shouldn't use the obsolete \texttt{eqnarray} environment, see
-Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
-\begin{align}
-f(x) &= x^2 + x\label{eq:f}\\
-f'(x) &= 2x + 1\label{eq:df}
-\end{align}
-Unnumbered multi-lined equations can be displayed using the
-\texttt{align*} environment. For example:
-\begin{align*}
-f(x) &= (x+1)(x-1)\\
-&= x^2 - 1
-\end{align*}
-If you want to mix numbered with unnumbered lines use the
-\texttt{align} environment and suppress unwanted line numbers with
-\verb|\nonumber|. For example:
-\begin{align}
-y &= x^2 + 3x - 2x + 1\nonumber\\
-&= x^2 + x + 1\label{eq:y}
-\end{align}
-An equation that is too long to fit on a single line can be
-displayed using the \texttt{split} environment. 
-Text can be embedded in an equation using \verb|\text| or
-\verb|\intertext| (as used in \theoremref{thm:eigenpow}).
-See the \textsf{amsmath} documentation for further details.
-
-\subsection{Operator Names}
-\label{sec:op}
-
-Predefined operator names are listed in \tableref{tab:operatornames}.
-For additional operators, either use \verb|\operatorname|,
-for example $\operatorname{var}(X)$ or declare it with
-\verb|\DeclareMathOperator|, for example
-\begin{verbatim}
-\DeclareMathOperator{\var}{var}
-\end{verbatim}
-and then use this new command. If you want limits that go above and
-below the operator (like \verb|\sum|) use the starred versions
-(\verb|\operatorname*| or \verb|\DeclareMathOperator*|).
-
-\begin{table*}[htbp]
-\floatconts
-  {tab:operatornames}%
-  {\caption{Predefined Operator Names (taken from 
-   \textsf{amsmath} documentation)}}%
-  {%
-\begin{tabular}{rlrlrlrl}
-\cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
-\cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
-\cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
-\cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
-\cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
-\cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
-\cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
-\cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
-\cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
-\end{tabular}\par
-\begin{tabular}{rlrl}
-\cs{varlimsup} & $\varlimsup$ 
-& \cs{varinjlim} & $\varinjlim$\\
-\cs{varliminf} & $\varliminf$ 
-& \cs{varprojlim} & $\varprojlim$
-\end{tabular}
-}
-\end{table*}
-
-\section{Vectors and Sets}
-\label{sec:vec}
-
-Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
-(The original version of \cs{vec} can also be accessed using
-\cs{orgvec}, for example $\orgvec{x}$.)
-The \textsf{jmlr} class also provides \cs{set} to typeset a
-set. For example $\set{S}$.
-
-\section{Floats}
-\label{sec:floats}
-
-Floats, such as figures, tables and algorithms, are moving
-objects and are supposed to float to the nearest convenient
-location. Please don't force them to go in a particular place. In
-general it's best to use the \texttt{htbp} specifier and don't
-put the figure or table in the middle of a paragraph (that is
-make sure there's a paragraph break above and below the float).
-Floats are supposed to have a little extra space above and below
-them to make them stand out from the rest of the text. This extra
-spacing is put in automatically and shouldn't need modifying.
-
-If your article will later be reprinted in the Challenges for
-Machine Learning, please be aware that the CiML books use a
-different paper size, so if you want to resize any images use a
-scale relative to the line width (\verb|\linewidth|), text width
-(\verb|\textwidth|) or text height (\verb|\textheight|).
-
-To ensure consistency, please \emph{don't} try changing the format of the caption by doing
-something like:
-\begin{verbatim}
-\caption{\textit{A Sample Caption.}}
-\end{verbatim}
-or
-\begin{verbatim}
-\caption{\em A Sample Caption.}
-\end{verbatim}
-You can, of course, change the font for individual words or 
-phrases, for example:
-\begin{verbatim}
-\caption{A Sample Caption With Some \emph{Emphasized Words}.}
-\end{verbatim}
-
-\subsection{Tables}
-\label{sec:tables}
-
-Tables should go in the \texttt{table} environment. Within this
-environment use \verb|\floatconts| (defined by \textsf{jmlr})
-to set the caption correctly and center the table contents.
-The location of the caption depends on the \verb|tablecaption|
-setting in the document class options.
-
-\begin{table}[htbp]
- % The first argument is the label.
- % The caption goes in the second argument, and the table contents
- % go in the third argument.
-\floatconts
-  {tab:example}%
-  {\caption{An Example Table}}%
-  {\begin{tabular}{ll}
-  \bfseries Dataset & \bfseries Result\\
-  Data1 & 0.12345\\
-  Data2 & 0.67890\\
-  Data3 & 0.54321\\
-  Data4 & 0.09876
-  \end{tabular}}
-\end{table}
-
-If you want horizontal rules you can use the \textsf{booktabs}
-package which provides the commands \verb|\toprule|, 
-\verb|\midrule| and \verb|\bottomrule|. For example, see
-\tableref{tab:example-booktabs}.
-
-\begin{table}[hbtp]
-\floatconts
-  {tab:example-booktabs}
-  {\caption{A Table With Horizontal Lines}}
-  {\begin{tabular}{ll}
-  \toprule
-  \bfseries Dataset & \bfseries Result\\
-  \midrule
-  Data1 & 0.12345\\
-  Data2 & 0.67890\\
-  Data3 & 0.54321\\
-  Data4 & 0.09876\\
-  \bottomrule
-  \end{tabular}}
-\end{table}
-
-If you really want vertical lines as well, you can't use the
-\textsf{booktabs} commands as there'll be some unwanted gaps.
-Instead you can use \LaTeX's \verb|\hline|, but the rows may
-appear a bit cramped.  You can add extra space above or below a
-row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
-see \tableref{tab:example-hline}. However, you might want to read
-the \textsf{booktabs} documentation regarding the use of vertical
-lines.
-
-\begin{table}[htbp]
-\floatconts
-  {tab:example-hline}
-  {\caption{A Table With Horizontal and Vertical Lines}}%
-  {%
-    \begin{tabular}{|l|l|}
-    \hline
-    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
-    \abovestrut{2.2ex}Data1 & 0.12345\\
-    Data2 & 0.67890\\
-    Data3 & 0.54321\\
-    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
-    \end{tabular}
-  }
-\end{table}
-
-If you want to align numbers on their decimal point, you can
-use the \textsf{siunitx} package. For example, see
-\tableref{tab:example-siunitx}. For further details see the
-\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
-siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.
-
-\begin{table}[htbp]
-\floatconts
-  {tab:example-siunitx}
-  {\caption{A Table With Numbers Aligned on the Decimal Point}}
-  {\begin{tabular}{lS[tabformat=3.5]}
-  \bfseries Dataset & {\bfseries Result}\\
-  Data1 & 0.12345\\
-  Data2 & 10.6789\\
-  Data3 & 50.543\\
-  Data4 & 200.09876
-  \end{tabular}}
-\end{table}
-
-If the table is too wide, you can adjust the inter-column
-spacing by changing the value of \verb|\tabcolsep|. For
-example:
-\begin{verbatim}
-\setlength{\tabcolsep}{3pt}
-\end{verbatim}
-If the table is very wide but not very long, you can use the
-\texttt{sidewaystable} environment defined in the
-\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
-If the table is too long to fit on a page, you can use the
-\texttt{longtable} environment defined in the \textsf{longtable}
-package (so use \verb|\usepackage{longtable}|).
-
-\subsection{Figures}
-\label{sec:figures}
-
-Figures should go in the \texttt{figure} environment. Within this
-environment, use \verb|\floatconts| to correctly position the
-caption and center the image. Use \verb|\includegraphics|
-for external graphics files but omit the file extension. Do not
-use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
-image, it's better to use a fraction of the line width rather
-than an explicit length. For example, see \figureref{fig:nodes}.
-
-\begin{figure}[htbp]
- % Caption and label go in the first argument and the figure contents
- % go in the second argument
-\floatconts
-  {fig:nodes}
-  {\caption{Example Image}}
-  {\includegraphics[width=0.5\linewidth]{images/nodes}}
-\end{figure}
-
-If your image is made up of \LaTeX\ code (for example, commands
-provided by the \textsf{pgf} package) you can include it using
-\cs{includeteximage} (defined by the \textsf{jmlr} class). This
-can be scaled and rotated in the same way as \cs{includegraphics}.
-For example, see \figureref{fig:teximage}.
-
-\begin{figure}[htbp]
-\floatconts
-  {fig:teximage}
-  {\caption{Image Created Using \LaTeX\ Code}}
-  {\includeteximage[angle=45]{images/teximage}}
-\end{figure}
-
-If the figure is too wide to fit on the page, you can use the
-\texttt{sidewaysfigure} environment defined in the
-\textsf{rotating} package.
-
-Don't use \verb|\graphicspath|.\footnote{This is specific to the
-\textsf{jmlr} class, not a general recommendation. The main file
-that generates the proceedings or the CiML book is typically in a
-different directory to the imported articles, so it modifies the
-graphics path when it imports an article.} If the images 
-are contained in a subdirectory, specify this when you include the image, for
-example \verb|\includegraphics{figures/mypic}|.
-
-\subsubsection{Sub-Figures}
-\label{sec:subfigures}
-
-Sub-figures can be created using \verb|\subfigure|, which is
-defined by the \textsf{jmlr} class. The optional argument allows
-you to provide a subcaption. The label should be placed in the
-mandatory argument of \verb|\subfigure|. You can reference the
-entire figure, for example \figureref{fig:subfigex}, or you can
-reference part of the figure using \verb|\figureref|, for example
-\figureref{fig:circle}. Alternatively you can reference the
-subfigure using \verb|\subfigref|, for example
-\subfigref{fig:circle,fig:square} in \figureref{fig:subfigex}.
-
-\begin{figure}[htbp]
-\floatconts
-  {fig:subfigex}
-  {\caption{An Example With Sub-Figures.}}
-  {%
-    \subfigure[A Circle]{\label{fig:circle}%
-      \includegraphics[width=0.2\linewidth]{images/circle}}%
-    \qquad
-    \subfigure[A Square]{\label{fig:square}%
-      \includegraphics[width=0.2\linewidth]{images/square}}
-  }
-\end{figure}
-
-By default, the sub-figures are aligned on the baseline.
-This can be changed using the second optional argument
-of \verb|\subfigure|. This may be \texttt{t} (top), \texttt{c}
-(centered) or \texttt{b} (bottom). For example, the subfigures
-\subfigref{fig:circle2,fig:square2} in \figureref{fig:subfigex2}
-both have \verb|[c]| as the second optional argument.
-
-\begin{figure}[htbp]
-\floatconts
-  {fig:subfigex2}
-  {\caption{Another Example With Sub-Figures.}}
-  {%
-    \subfigure[A Small Circle][c]{\label{fig:circle2}%
-      \includegraphics[width=0.1\linewidth]{images/circle}}%
-    \qquad
-    \subfigure[A Square][c]{\label{fig:square2}%
-      \includegraphics[width=0.2\linewidth]{images/square}}
-  }
-\end{figure}
-
-\subsection{Sub-Tables}
-\label{sec:subtables}
-There is an analogous command \verb|\subtable| for sub-tables.
-It has the same syntax as \verb|\subfigure| described above.
-You can reference the table using \verb|\tableref|, for example
-\tableref{tab:subtabex} or you can reference part of the table,
-for example \tableref{tab:ab}. Alternatively you can reference the
-subtable using \verb|\subtabref|, for example
-\subtabref{tab:ab,tab:cd} in \tableref{tab:subtabex}.
-
-\begin{table}[htbp]
-\floatconts
- {tab:subtabex}
- {\caption{An Example With Sub-Tables}}
- {%
-   \subtable{%
-     \label{tab:ab}%
-     \begin{tabular}{cc}
-     \bfseries A & \bfseries B\\
-     1 & 2
-     \end{tabular}
-   }\qquad
-   \subtable{%
-     \label{tab:cd}%
-     \begin{tabular}{cc}
-     \bfseries C & \bfseries D\\
-     3 & 4\\
-     5 & 6
-     \end{tabular}
-   }
- }
-\end{table}
-
-By default, the sub-tables are aligned on the top.
-This can be changed using the second optional argument
-of \verb|\subtable|. This may be \texttt{t} (top), \texttt{c}
-(centered) or \texttt{b} (bottom). For example, the sub-tables
-\subtabref{tab:ab2,tab:cd2} in \tableref{tab:subtabex2}
-both have \verb|[c]| as the second optional argument.
-
-\begin{table}[htbp]
-\floatconts
- {tab:subtabex2}
- {\caption{Another Example With Sub-Tables}}
- {%
-   \subtable[][c]{%
-     \label{tab:ab2}%
-     \begin{tabular}{cc}
-     \bfseries A & \bfseries B\\
-     1 & 2
-     \end{tabular}
-   }\qquad
-   \subtable[][c]{%
-     \label{tab:cd2}%
-     \begin{tabular}{cc}
-     \bfseries C & \bfseries D\\
-     3 & 4\\
-     5 & 6
-     \end{tabular}
-   }
- }
-\end{table}
-
-\subsection{Algorithms}
-\label{sec:algorithms}
-
-Enumerated textual algorithms can be displayed using the
-\texttt{algorithm} environment. Within this environment, use
-\verb|\caption| to set the caption and you can use an
-\texttt{enumerate} or nested \texttt{enumerate} environments.
-For example, see \algorithmref{alg:gauss}. Note that algorithms
-float like figures and tables.
-
-\begin{algorithm}[htbp]
-\floatconts
-  {alg:gauss}%
-  {\caption{The Gauss-Seidel Algorithm}}%
-{%
-\begin{enumerate}
-  \item For $k=1$ to maximum number of iterations
-    \begin{enumerate}
-      \item For $i=1$ to $n$
-        \begin{enumerate}
-        \item $x_i^{(k)} = 
-          \frac{b_i - \sum_{j=1}^{i-1}a_{ij}x_j^{(k)}
-          - \sum_{j=i+1}^{n}a_{ij}x_j^{(k-1)}}{a_{ii}}$
-        \item If $\|\vec{x}^{(k)}-\vec{x}^{(k-1)} < \epsilon\|$,
-          where $\epsilon$ is a specified stopping criteria, stop.
+Figures 6-8 are computed ultizing the equation for relative tremor: $r_\SUP{ET}^i - r_\SUP{HT}^\SUP{i-D+1}|$
+\item F6: Maximum ET
+\item F7: Minimum ET
+\item F8: Standard Deviation of ET values
+\item F9: The number of times the difference between HT and ET radii changes from positive to negative.
 \end{enumerate}
-    \end{enumerate}
-\end{enumerate}
-}%
-\end{algorithm}
-
-If you'd rather have the same numbering throughout the algorithm
-but still want the convenient indentation of nested 
-\texttt{enumerate} environments, you can use the
-\texttt{enumerate*} environment provided by the \textsf{jmlr}
-class. For example, see \algorithmref{alg:moore}.
-
-\begin{algorithm}
-\floatconts
-  {alg:moore}%
-  {\caption{Moore's Shortest Path}}%
-{%
-Given a connected graph $G$, where the length of each edge is 1:
-\begin{enumerate*}
-  \item Set the label of vertex $s$ to 0
-  \item Set $i=0$
-  \begin{enumerate*}
-    \item \label{step:locate}Locate all unlabelled vertices 
-          adjacent to a vertex labelled $i$ and label them $i+1$
-    \item If vertex $t$ has been labelled,
-    \begin{enumerate*}
-      \item[] the shortest path can be found by backtracking, and 
-      the length is given by the label of $t$.
-    \end{enumerate*}
-    otherwise
-    \begin{enumerate*}
-      \item[] increment $i$ and return to step~\ref{step:locate}
-    \end{enumerate*}
-  \end{enumerate*}
-\end{enumerate*}
-}%
-\end{algorithm}
-
-Pseudo code can be displayed using the \texttt{algorithm2e}
-environment. This is defined by the \textsf{algorithm2e} package
-(which is automatically loaded) so check the \textsf{algorithm2e}
-documentation for further details.\footnote{Either \texttt{texdoc
-algorithm2e} or \url{http://www.ctan.org/pkg/algorithm2e}}
-For an example, see \algorithmref{alg:net}.
-
-\begin{algorithm2e}
-\caption{Computing Net Activation}
-\label{alg:net}
- % older versions of algorithm2e have \dontprintsemicolon instead
- % of the following:
- %\DontPrintSemicolon
- % older versions of algorithm2e have \linesnumbered instead of the
- % following:
- %\LinesNumbered
-\KwIn{$x_1, \ldots, x_n, w_1, \ldots, w_n$}
-\KwOut{$y$, the net activation}
-$y\leftarrow 0$\;
-\For{$i\leftarrow 1$ \KwTo $n$}{
-  $y \leftarrow y + w_i*x_i$\;
-}
-\end{algorithm2e}
-
-\section{Description Lists}
-
-The \textsf{jmlr} class also provides a description-like 
-environment called \texttt{altdescription}. This has an
-argument that should be the widest label in the list. Compare:
-\begin{description}
-\item[add] A method that adds two variables.
-\item[differentiate] A method that differentiates a function.
-\end{description}
-with
-\begin{altdescription}{differentiate}
-\item[add] A method that adds two variables.
-\item[differentiate] A method that differentiates a function.
-\end{altdescription}
-
-\section{Theorems, Lemmas etc}
-\label{sec:theorems}
-
-The following theorem-like environments are predefined by
-the \textsf{jmlr} class: \texttt{theorem}, \texttt{example},
-\texttt{lemma}, \texttt{proposition}, \texttt{remark}, 
-\texttt{corollary}, \texttt{definition}, \texttt{conjecture}
-and \texttt{axiom}. You can use the \texttt{proof} environment
-to display the proof if need be, as in \theoremref{thm:eigenpow}.
-
-\begin{theorem}[Eigenvalue Powers]\label{thm:eigenpow}
-If $\lambda$ is an eigenvalue of $\vec{B}$ with eigenvector
-$\vec{\xi}$, then $\lambda^n$ is an eigenvalue of $\vec{B}^n$
-with eigenvector $\vec{\xi}$.
-\begin{proof}
-Let $\lambda$ be an eigenvalue of $\vec{B}$ with eigenvector
-$\xi$, then
-\begin{align*}
-\vec{B}\vec{\xi} &= \lambda\vec{\xi}
-\intertext{premultiply by $\vec{B}$:}
-\vec{B}\vec{B}\vec{\xi} &= \vec{B}\lambda\vec{\xi}\\
-\Rightarrow \vec{B}^2\vec{\xi} &= \lambda\vec{B}\vec{\xi}\\
-&= \lambda\lambda\vec{\xi}\qquad
-\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
-&= \lambda^2\vec{\xi}
-\end{align*}
-Therefore true for $n=2$. Now assume true for $n=k$:
-\begin{align*}
-\vec{B}^k\vec{\xi} &= \lambda^k\vec{\xi}
-\intertext{premultiply by $\vec{B}$:}
-\vec{B}\vec{B}^k\vec{\xi} &= \vec{B}\lambda^k\vec{\xi}\\
-\Rightarrow \vec{B}^{k+1}\vec{\xi} &= \lambda^k\vec{B}\vec{\xi}\\
-&= \lambda^k\lambda\vec{\xi}\qquad
-\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
-&= \lambda^{k+1}\vec{\xi}
-\end{align*}
-Therefore true for $n=k+1$. Therefore, by induction, true for all
-$n$.
-\end{proof}
-\end{theorem}
-
-\begin{lemma}[A Sample Lemma]\label{lem:sample}
-This is a lemma.
-\end{lemma}
-
-\begin{remark}[A Sample Remark]\label{rem:sample}
-This is a remark.
-\end{remark}
-
-\begin{corollary}[A Sample Corollary]\label{cor:sample}
-This is a corollary.
-\end{corollary}
-
-\begin{definition}[A Sample Definition]\label{def:sample}
-This is a definition.
-\end{definition}
-
-\begin{conjecture}[A Sample Conjecture]\label{con:sample}
-This is a conjecture.
-\end{conjecture}
-
-\begin{axiom}[A Sample Axiom]\label{ax:sample}
-This is an axiom.
-\end{axiom}
-
-\begin{example}[An Example]\label{ex:sample}
-This is an example.
-\end{example}
-
-\section{Color vs Grayscale}
-\label{sec:color}
-
-It's helpful if authors supply grayscale versions of their
-images in the event that the article is to be incorporated into
-a black and white printed book. With external PDF, PNG or JPG
-graphic files, you just need to supply a grayscale version of the
-file. For example, if the file is called \texttt{myimage.png},
-then the gray version should be \texttt{myimage-gray.png} or
-\texttt{myimage-gray.pdf} or \texttt{myimage-gray.jpg}. You don't
-need to modify your code. The \textsf{jmlr} class checks for
-the existence of the grayscale version if it is print mode 
-(provided you have used \verb|\includegraphics| and haven't
-specified the file extension).
-
-You can use \verb|\ifprint| to determine which mode you are in.
-For example, in \figureref{fig:nodes}, the 
-\ifprint{dark gray}{purple} ellipse represents an input and the
-\ifprint{light gray}{yellow} ellipse represents an output.
-Another example: {\ifprint{\bfseries}{\color{red}}important text!}
-
-You can use the class option \texttt{gray} to see how the
-document will appear in gray scale mode. \textcolor{blue}{Colored
-text} will automatically be converted to gray scale in print mode.
-
-The \textsf{jmlr} class loads the \textsf{xcolor}
-package, so you can also define your own colors. For example:
-\ifprint
-  {\definecolor{myred}{gray}{0.5}}%
-  {\definecolor{myred}{rgb}{0.5,0,0}}%
-\textcolor{myred}{XYZ}.
-
-The \textsf{xcolor} class is loaded with the \texttt{x11names}
-option, so you can use any of the x11 predefined colors (listed
-in the \textsf{xcolor} documentation\footnote{either 
-\texttt{texdoc xcolor} or \url{http://www.ctan.org/pkg/xcolor}}).
-
-\section{Citations and Bibliography}
-\label{sec:cite}
-
-The \textsf{jmlr} class automatically loads \textsf{natbib}
-and automatically sets the bibliography style, so you don't need to
-use \verb|\bibliographystyle|.
-This sample file has the citations defined in the accompanying
-BibTeX file \texttt{jmlr-sample.bib}. For a parenthetical
-citation use \verb|\citep|. For example
-\citep{guyon-elisseeff-03}. For a textual citation use
-\verb|\citet|. For example \citet{guyon2007causalreport}. 
-Both commands may take a comma-separated list, for example
-\citet{guyon-elisseeff-03,guyon2007causalreport}.
-
-These commands have optional arguments and have a starred
-version. See the \textsf{natbib} documentation for further
-details.\footnote{Either \texttt{texdoc natbib} or
-\url{http://www.ctan.org/pkg/natbib}}
-
-The bibliography is displayed using \verb|\bibliography|.
-
-\acks{Acknowledgements go here.}
-
-\bibliography{jmlr-sample}
-
-\appendix
-
-\section{First Appendix}\label{apd:first}
-
-This is the first appendix.
-
-\section{Second Appendix}\label{apd:second}
-
-This is the second appendix.
 

### 2021-09-12 Submission/Paper/Paper.tex
table 1 done

@@
 
+% table 1
+\begin{table*}[hbtp]
+\centering 
+\floatconts
+{tab:table1}
+{\caption{Demographics of Data}} 
+    {
+        \begin{tabular}{lcccccc}
+        \toprule
+        \bfseries & \bfseries Mean Age (SD) & \bfseries Left Handed & \bfseries Right Handed & \bfseries \% Female & \bfseries Counts \\
+        \midrule
+        Healthy & 44.11 (15.46) & 7 & 46 & 54.7\% & 53 \\
+        Healthy & 58.75 (7.51) & 5 & 69 & 20.3\% & 74 \\
+        \bottomrule
+        \end{tabular}
+    }
+\end{table*}
+
 \paragraph{Preprocessing}
@@
 
+The features were then normalized as follows:
+\[f[i]' = \sum_\SUP{i=1}^9\frac{f[i] - avg(i)}{std(i)}\]
+f[i]' represents the normalized equivalent of feature f[i] for features 1-9.
+
+Additionally, we noticed there was a large class-imbalance present in our dataset, with 53 healthy and 105 PD patients.
+After performing experiments with our machine learning models, we discovered that this imbalance led to overfitting and undesirable accuracies, even after the assignation of higher weight to the healthy class.
+To cope with this, we truncated our original dataset by removing the 31 PD patients from the New HandPD dataset.
+This resulted in 127 patients, 53 healthy and 74 PD, which greatly boosted our results.
+Table \ref{tab:table1} shows our demographics for cohort of patients.
+
 \end{document}

### 2021-09-12 Submission/Paper/Paper.tex
methods done

@@
 This resulted in 127 patients, 53 healthy and 74 PD, which greatly boosted our results.
+The final dataset of 158 patients was randomly split between train (76.5\%), validation (8.5\%) and hold-out test (15\%) sets.
 Table \ref{tab:table1} shows our demographics for cohort of patients.
+\section{Methodology}
+\label{Methodology}
+
+\label{sec:SVM}  
+\paragraph{(1) Support Vector Machines on Numerical Features Dataset} In model 1, we utilized a Support Vector Machine (SVM) where the PD diagnosis label was analyzed on the nine extracted numerical features.
+We used 10-fold Cross-Validation (CV) on the held-out validation set to maximize Accuracy by choosing an optimal kernel (Radial Base, Linear, or Polynomial), class weightage (None or Balanced), probability threshold and lambda.
+After training and validating the model on the image level, we tested it on the patient-level, extracting all 8 images from 11 PD and 8 healthy patients (15\% test set) and selecting an optimal aggregation scheme for patient-level predictions.
+
+\label{sec:LogReg}  
+\paragraph{(2) Regularized Logistic Regression on Numerical Features Dataset} In model 2, we employed Regularized Logistic Regression strategies, regressing the PD diagnosis label against the nine extracted numerical features.
+With 10-fold CV, we iterated over different lambda values, probability thresholds, and loss and solver functions to maximize accuracy for our image-level predictions.
+We tested the model on the patient-level After training and validating the model on the image level, we tested it on the patient-level, extracting all 8 images from 5 PD and 4 healthy patients (15\% test set) and selecting an optimal aggregation scheme for patient-level predictions.
+
+\section{Results}
+\label{Results}
 

### 2021-09-12 Submission/Paper/Paper.tex
added results table and conclusion + future works

@@
 Ming Wang \SUP{3},
-Lijun Zhang \SUP{4},
+Lijun Zhang \SUP{4}
 \centering \Email{
@@
 Table \ref{tab:table1} shows our demographics for cohort of patients.
+
+% table 2
+\begin{table*}[hbtp]
+\centering 
+\floatconts
+{tab:table2}
+{\caption{Model Performance} }
+    {
+        \begin{tabular}{lcccccccccc}
+        \toprule
+        \bfseries Model & \bfseries ACC & \bfseries AUC & \bfseries FP & \bfseries FN & \bfseries Sensitivity & \bfseries Specificity & \bfseries PPV & \bfseries NPV & \bfseries Threshold \\
+        \midrule
+        SVM & 0.92 & 0.93 & 12 & 0 & 1.0 & 0.81 & 0.89 & 1.0 & 0.65 \\
+        Logistic Regression & 0.93 & 0.96 & 3 & 7 & 0.92 & 0.95 & 0.90 & 0.96 & 0.62 \\
+        \bottomrule
+        \end{tabular}
+    }
+\end{table*}
+
 \section{Methodology}
@@
 
+\section{Conclusion and Future Works}
+\label{Conclusion+FutureWorks} In this work, we applied classification algorithms to the task of diagnosing Parkinson's Disease using handwriting samples.
+Our dataset was relatively small in size, a problem we hope to address in the future through development of a web portal.
+Along with our models, we devised a handwriting assessment based on precedents in this research area as well as data available to us.
+Once this portal is complete, we hope to perform clinical studies with our partners from Penn State University to evaluate the handwriting assessment and develop data considering temporal stages of Parkinson’s Disease-by analyzing handwriting images from early and later stages of Parkinson’s.
+
+Furthermore, we hope to increase the accessibility of our handwriting assessment through online availability using a touch-screen device, such as a phone or tablet.
+This enables us to take advantage of signals provided by such a device.
+A similar exercise may be performed using keystroke data from a computer and asking a patient to type, rather than draw.
+The next iteration of this work aspires to further improve model performance and work toward automatic and real-time detection of Parkinson’s disease.
+
 \end{document}

### 2021-09-12 Submission/Paper/Paper.tex
added citations (might need more but couldn't think of any more)

@@
  % The optional argument of \title is used in the header
-\title[Short Title]{Full Title of Article\titlebreak This Title Has
-A Line Break}
+\title[Machine Learning for Diagnosis of Parkinson's Disease]{Machine Learning Real-Time and Automatic Diagnosis of Parkinson’s Disease by Extracting Signs of Micrographia from Handwriting Images}
 
@@
 In order to establish mechanisms for early detection of PD, we applied machine and deep learning techniques to extract signs of micrographia from drawing samples gathered from a variety of open-source datasets.
-We have discovered that a Convolutional Neural Network (CNN) performs best and can reliably learn important information solely from raw images.
 This work sets the foundations for a web portal allowing any individual worldwide with access to a pen, printer, and phone to upload an image of a handwriting assessment we designed and receive a PD diagnosis in real-time.
 \end{abstract}
+
 \begin{keywords}
-CNN, Parkinson’s, PD, micrographia, disorder, early detection, diagnosis, neurodegenerative
+Parkinson’s, Micrographia, Early Detection, Diagnosis, Neurodegenerative
 \end{keywords}
@@
 Tools that can make the diagnosis process accurate, accessible, automatic, real-time, early, and free of cost can have tremendous impact for Parkinson’s patients.
-In this study, we apply machine and deep learning strategies on a variety of data, including both image and numerical features.
-We present a Convolutional Neural Network model able to uncover signs of Parkinson’s in drawing images and compare it to machine learning models.
+In this study, we apply machine learning strategies to obtain and accurate and early detection of Parkinson's disease.
 
@@
 Prior works have incorporated the use of voice recordings, electroencephalogram (EEG) signals, and smart devices to create models that deduce whether a patient has PD or not.
-Zhao et al.
-hypothesized that patients with PD exhibit deficits in the production of emotional speech.
+\citep{zhao2014automatic} hypothesized that patients with PD exhibit deficits in the production of emotional speech.
 To test this conjecture, five patients and seven healthy individuals were used to recognize Parkinson’s disease through voice recordings.
 Naive Bayes, Random Forests, and Support Vector Machines were applied for classification, achieving 65.5\% and 73.33\% accuracies on classifying PD and control.
-Oh et al.
-utilized EEG signals and a Convolutional Neural Network (CNN) to detect PD
+\citep{oh2020deep} utilized EEG signals and a Convolutional Neural Network (CNN) to detect PD
 by assessing whether the EEG signals depicted brain abnormalities, achieving 88.25\% accuracy.
-Drotár et al.
-employed the use of a digitizing tablet to assess both in-air and on-surface kinematic variables during handwriting of a sentence in 37 PD patients on medication and 38 age- and gender-matched healthy controls.
+\citep{drotar2014analysis} employed the use of a digitizing tablet to assess both in-air and on-surface kinematic variables during handwriting of a sentence in 37 PD patients on medication and 38 age and gender-matched healthy controls.
 Using Support Vector Machines, an accuracy of 85.61\% was achieved.
-These studies require patients to visit a neurologist to access a smart device and undergo various scans like EEG and PET, making the process expensive, time-consuming, and difficult to access.
+However, these studies require patients to visit a neurologist to access a smart device and undergo various scans like EEG and PET, making the process expensive, time-consuming, and difficult to access.
 In this study, we aim to make the PD diagnosis process accurate, efficient, and accessible by using images of handwriting samples to automate the PD diagnosis process.
@@
 \paragraph{Dataset}
-\label{sec:Dataset} Our dataset was formed by combining the New HandPD and Old HandPD dataset available at (https://wwwp.fc.unesp.br/~papa/pub/datasets/Handpd/).
-It consists of 158 individuals, 53 healthy and 105 PD patients.
+\label{sec:Dataset} Our dataset was formed by combining the New HandPD and Old HandPD dataset \citep{pereira2016new}.
+It consisted of 158 individuals, 53 healthy and 105 PD patients.
 Each patient drew 8 images, 4 spirals and 4 meander.
@@
 \label{sec:Preprocessing} 
-We mimicked the feature extraction process used (cite handpd ppl) to extract 9 numerical features from the images.
+We mimicked the feature extraction process used \citep{pereira2016new} to extract 9 numerical features from the images.
 First, the handwritten trace (HT) and exam trace (ET) were extracted from the image.
@@
 
-Figures 6-8 are computed ultizing the equation for relative tremor: $r_\SUP{ET}^i - r_\SUP{HT}^\SUP{i-D+1}|$
+Figures 6-8 are computed utilizing the equation for relative tremor: $r_\SUP{ET}^i - r_\SUP{HT}^\SUP{i-D+1}|$
 \item F6: Maximum ET
@@
 \label{sec:SVM}  
-\paragraph{(1) Support Vector Machines on Numerical Features Dataset} In model 1, we utilized a Support Vector Machine (SVM) where the PD diagnosis label was analyzed on the nine extracted numerical features.
-We used 10-fold Cross-Validation (CV) on the held-out validation set to maximize Accuracy by choosing an optimal kernel (Radial Base, Linear, or Polynomial), class weightage (None or Balanced), probability threshold and lambda.
+\paragraph{(1) Support Vector Machines on Numerical Features Dataset} In model 1, we utilized a Support Vector Machine (SVM) \citep{708428} where the PD diagnosis label was analyzed on the nine extracted numerical features.
+We used 10-fold Cross-Validation (CV) on the held-out validation set to maximize accuracy by choosing an optimal kernel (Radial Base, Linear, or Polynomial), class weightage (None or Balanced), probability threshold and lambda.
 After training and validating the model on the image level, we tested it on the patient-level, extracting all 8 images from 11 PD and 8 healthy patients (15\% test set) and selecting an optimal aggregation scheme for patient-level predictions.
@@
 \label{sec:LogReg}  
-\paragraph{(2) Regularized Logistic Regression on Numerical Features Dataset} In model 2, we employed Regularized Logistic Regression strategies, regressing the PD diagnosis label against the nine extracted numerical features.
+\paragraph{(2) Regularized Logistic Regression on Numerical Features Dataset} In model 2, we employed Regularized Logistic Regression \citep{tibshirani1996regression} strategies, regressing the PD diagnosis label against the nine extracted numerical features.
 With 10-fold CV, we iterated over different lambda values, probability thresholds, and loss and solver functions to maximize accuracy for our image-level predictions.
-We tested the model on the patient-level After training and validating the model on the image level, we tested it on the patient-level, extracting all 8 images from 5 PD and 4 healthy patients (15\% test set) and selecting an optimal aggregation scheme for patient-level predictions.
+After training and validating the model on the image level, we tested it on the patient-level, extracting all 8 images from 5 PD and 4 healthy patients (15\% test set) and selecting an optimal aggregation scheme for patient-level predictions.
 
@@
 
+\clearpage
+
+% References
+\bibliography{jmlr-sample}
+\nocite{*}
+
+\clearpage
 \end{document}

### 2021-09-14 Submission/Paper/Paper.tex
updated progress

@@
 
+\usepackage[table]{xcolor}
+\newcommand\red[1]{{\color{red}#1}}
+
  % The following command is just for this sample document:
@@
  % The optional argument of \title is used in the header
-\title[Machine Learning for Diagnosis of Parkinson's Disease]{Machine Learning Real-Time and Automatic Diagnosis of Parkinson’s Disease by Extracting Signs of Micrographia from Handwriting Images}
+\title[Machine Learning for Diagnosis of Parkinson's Disease]{Machine Learning for Real-Time, Automatic, and Early Diagnosis of Parkinson’s Disease by Extracting Signs of Micrographia from Handwriting Images}
 
 % Authors with different addresses and equal first authors:
-\author{Riya Tyagi \nametag{\thanks{Authors contributed equally}\SUP{1}},
-Tanish Tyagi \nametag{\footnotemark[1]\SUP{2}}, 
-Ming Wang \SUP{3},
-Lijun Zhang \SUP{4}
-\centering \Email{
-\\[\bigskipamount] 
-\SUP{1}\{rtyagi\}
-@exeter.edu}
-\centering \Email{
-\\[\bigskipamount] 
-\SUP{2}\{ttyagi\}@mgh.harvard.edu}
-\centering \Email{
-\\[\bigskipamount] 
-\SUP{3}\{mwang\}@phs.psu.edu}
-\centering \Email{
-\\[\bigskipamount] 
-\SUP{4}\{lzhang6\}@pennstatehealth.psu.edu}
-}
+% \author{Riya Tyagi \nametag{\thanks{Authors contributed equally}},
+% Tanish Tyagi \nametag{\footnotemark[1]}, 
+% Ming Wang,
+% Lijun Zhang
+% \centering \Email{ 
+% \\[\bigskipamount]  
+% rtyagi@exeter.edu, ttyagi@mgh.harvard.edu, mwang@phs.psu.edu, lzhang6@pennstathealth.psu.edu}
+% }
 
@@
 \begin{abstract}
-Parkinson’s disease (PD) is debilitating, progressive, and clinically marked by motor symptoms, which affects over 10 million lives around the world.
-As the second most common neurodegenerative disease with no approved treatments, the existing diagnosis methods have limitations, such as the expense of visiting doctors and the challenge of automated early detection, considering that symptoms and behavioral differences in patients and healthy individuals are often not present in early stages.
+Parkinson’s disease (PD) is debilitating, progressive, and clinically marked by motor symptoms.
+As the second most common neurodegenerative disease and with no approved treatments, it affects over 10 million lives around the world.
+Existing diagnoses methods have limitations, such as the expense of visiting doctors and the challenge of automated early detection, considering that behavioral differences in patients and healthy individuals are often indistinguishable in early stages.
 Micrographia is a disorder commonly observed in early stages of PD.
-In order to establish mechanisms for early detection of PD, we applied machine and deep learning techniques to extract signs of micrographia from drawing samples gathered from a variety of open-source datasets.
-This work sets the foundations for a web portal allowing any individual worldwide with access to a pen, printer, and phone to upload an image of a handwriting assessment we designed and receive a PD diagnosis in real-time.
+In order to establish mechanisms for early detection of PD, we applied machine learning techniques to extract signs of micrographia from drawing samples gathered from two open-source datasets, achieving a predictive accuracy of 94\%.
+This work also sets the foundations for a publicly available and user-friendly web portal that anyone with access to a pen, printer, and phone can use for early detection of PD.
 \end{abstract}
@@
 \begin{keywords}
-Parkinson’s, Micrographia, Early Detection, Diagnosis, Neurodegenerative
+Parkinson’s Disease, Machine Learning, Micrographia, Early Detection, Predictive accuracy
 \end{keywords}
@@
 
-Parkinson’s disease (PD) is a degenerative, chronic, and progressive nervous system disorder that affects movement.
+Parkinson’s disease (PD) is a neurodegenerative, chronic, and progressive nervous system disorder that affects movement.
 More than 10 million people worldwide are currently living with PD, and the number of cases is expected to more than double in the next decade.
-Symptoms include tremors, slowness of movement, stiffness, and changes in writing skills.
+\citep{choi2017refining} Symptoms include tremors, slowness of movement, stiffness, and changes in writing skills.
 PD occurs when dopamine-producing nerve cells die, a process that can take almost 10 years to reach its late and most severe stages.
@@
 
-Parkinson’s disease cannot be treated, although specific drugs and medications can assist with symptoms in early stages, potentially preventing the disease’s progression to more severe stages.
+Parkinson's Disease cannot be treated, although specific drugs and medications can assist with symptoms in early stages, potentially preventing the disease’s progression to more severe stages.
 Early detection and prognosis of PD are crucial for assisting patients to retain a good quality of life.
-However, diagnosing Parkinson’s disease in its early stages is a very challenging task, and there are currently no specific tests designed to diagnose PD.
+However, diagnosing Parkinson’s disease in its early stages is a very challenging task, and there are currently no specific tests designed to diagnose PD \citep{national_institute_of_neurological_disorders_and_stroke}.
 Diagnosis is based on a thorough examination performed by a trained medical official, including a neurological examination, medical history evaluation, blood and laboratory tests, and brain scans.
 Even with these procedures, PD is misdiagnosed up to 30\% of the time, especially in early stages, due to the many Parkinson’s mimics, the main ones being Essential Tremors and Drug Induced Parkinson’s.
-Additionally, up to 20\% of PD patients are undiagnosed.
+Additionally, up to 20\% of PD patients are undiagnosed \citep{schrag_ben-shlomo_quinn_2002}.
 Receiving a PD diagnosis is expensive, time consuming, and non-accessible, as reported by 21\% of patients who had to visit their general provider thrice before receiving a specialist referral for their condition.
+\citep{gavidia_2020}
 
 Tools that can make the diagnosis process accurate, accessible, automatic, real-time, early, and free of cost can have tremendous impact for Parkinson’s patients.
-In this study, we apply machine learning strategies to obtain and accurate and early detection of Parkinson's disease.
+In this study, we apply machine learning strategies for PD prediction based upon the existing drawing samples resources of micrographia.
 
@@
 Naive Bayes, Random Forests, and Support Vector Machines were applied for classification, achieving 65.5\% and 73.33\% accuracies on classifying PD and control.
-\citep{oh2020deep} utilized EEG signals and a Convolutional Neural Network (CNN) to detect PD
-by assessing whether the EEG signals depicted brain abnormalities, achieving 88.25\% accuracy.
+\citep{oh2020deep} utilized EEG signals and a Convolutional Neural Network (CNN) to detect PD by assessing whether the EEG signals depicted brain abnormalities, achieving 88.25\% accuracy.
 \citep{drotar2014analysis} employed the use of a digitizing tablet to assess both in-air and on-surface kinematic variables during handwriting of a sentence in 37 PD patients on medication and 38 age and gender-matched healthy controls.
@@
 However, these studies require patients to visit a neurologist to access a smart device and undergo various scans like EEG and PET, making the process expensive, time-consuming, and difficult to access.
-In this study, we aim to make the PD diagnosis process accurate, efficient, and accessible by using images of handwriting samples to automate the PD diagnosis process.
+In this study, we aim to make the PD diagnosis process more accurate, efficient, and accessible by using images of handwriting samples to automate the PD diagnosis process.
 
@@
 With these images, we constructed 2 datasets, one consisting of extracted numerical features and the other consisting of images.
+The process of assembling the image dataset and its uses are discussed further in Appendix ....
 
@@
         Healthy & 44.11 (15.46) & 7 & 46 & 54.7\% & 53 \\
-        Healthy & 58.75 (7.51) & 5 & 69 & 20.3\% & 74 \\
+        PD & 58.75 (7.51) & 5 & 69 & 20.3\% & 74 \\
         \bottomrule
@@
 \begin{enumerate}
+% \red{it is better to show some notation first or explain the notation after each formula. Otherwise, the reviewers will get confused.} 
 \item The root mean square (RMS) of the differences between the HT and ET radii.
 The radius of the HT or ET can be defined as the length of the straight line that connects an arbitrary point to the center of the HT or ET and is shown in figure (X).
-$N$ is the number of sample points on the HT and ET.
 \[RMS = \sqrt{\frac{1}{N} * \sum_\SUP{i=1}^N(r_\SUP{HT}^i - r_\SUP{ET}^i)^2}\]
+
+$N$ is the number of sample points on the HT and ET, and $r_\SUP{HT}^i$ + $r_\SUP{ET}^i$ denote the HT and ET radii for the $i$th point.
 
@@
 
+% \red{you may want to remove F3, F4, etc below}
 \item F3: The minimum difference between the HT and ET radii. 
@@
 
-\item F5: The Mean Relative Tremor (mrt) of a given individual’s HT.
+\item F5: The Mean Relative Tremor (MRT) of a given individual’s HT.
 This is defined as the mean difference between the radius of a given sample and its D left-nearest neighbors.
@@
 
-Figures 6-8 are computed utilizing the equation for relative tremor: $r_\SUP{ET}^i - r_\SUP{HT}^\SUP{i-D+1}|$
+Figures 6-8 are computed utilizing the equation for relative tremor: $|r_\SUP{ET}^i - r_\SUP{HT}^\SUP{i-D+1}|$
 \item F6: Maximum ET
@@
 {tab:table2}
-{\caption{Model Performance} }
+{\caption{Model Performance}}
     {
@@
 
-\section{Methodology}
+\begin{figure*}[hbtp]
+\centering
+\floatconts
+{fig:fig1}
+{\caption{Regularized Logistic Regression (left) and Support Vector Machines (right) ROC Curves}}
+
+    \subfloat{{\includegraphics[scale = 0.55]{images/logreg_roc.png} }}%
+    \subfloat{\includegraphics[scale = 0.55]{images/svm_roc.png}} %
+
+\end{figure*}
+
+\section{Methods}
 \label{Methodology}
@@
 \paragraph{(1) Support Vector Machines on Numerical Features Dataset} In model 1, we utilized a Support Vector Machine (SVM) \citep{708428} where the PD diagnosis label was analyzed on the nine extracted numerical features.
-We used 10-fold Cross-Validation (CV) on the held-out validation set to maximize accuracy by choosing an optimal kernel (Radial Base, Linear, or Polynomial), class weightage (None or Balanced), probability threshold and lambda.
+We used 10-fold Cross-Validation (CV) \citep{stone1974cross} on the held-out validation set to maximize accuracy by choosing an optimal kernel (Radial Base, Linear, or Polynomial), class weight (None or Balanced), probability threshold and lambda.
 After training and validating the model on the image level, we tested it on the patient-level, extracting all 8 images from 11 PD and 8 healthy patients (15\% test set) and selecting an optimal aggregation scheme for patient-level predictions.
@@
 \section{Results}
-\label{Results}
+\label{Results} To maximize the performance of both models, we utilized a probability threshold.
+First, we trained, validated, and tested the models on the image-level.
+All performance metrics in Table \ref{tab:table2} are based on image-level class assignments.
+
+However, our web portal will consider 6 - 8 different drawings per patient in the diagnosis process.
+To mimic this functionality, we tested each model on the patient-level with an aggregation scheme.
+We chose an optimal scheme from three options: applying a PD label to a patient if the model diagnosed 2/8 images as signs of PD, if the averaged probability score from all 8 images was greater than 0.5, or if the model predicted more than half the images to belong to a PD patient.
+The last scheme performed best, likely because the model tended to predict only a few images incorrectly per patient.
+
+Both models received the same patient-level accuracy: 0.9444.
+Additionally, we compared their Receiver Operating Characteristic (ROC) curves (Figure \ref{fig:fig1}) when tested on 10 different random selections of 19 patients (11 PD and 8 Control).
+Both models performed similarly on each test set, although Regularized Logistic Regression was more consistent because of the regularization applied.
+
+The best hyperparameters for the SVM model were:
+\begin{itemize}
+\item kernel = ‘rbf’, transforms radial data so it can be separated with a linear separation boundary
+\item class\_weight = ‘balanced’, adds weight to each class depending on the class balance
+\item C = 100, lambda value
+\end{itemize}
+
+The best hyperparameters for the Regularized Logistic Regression model were:
+\begin{itemize}
+\item penalty = ‘elasticnet’, a combination of L1 and L2 Regularization
+\item l1\_ratio = 0.75, uses 75\% L1 Regularization, 25\% L2 Regularization
+\item solver = ‘saga’, only solver which supports ‘elasticnet’ penalty, the best-performer
+\item C = 0.1, lambda value
+\item class\_weight = ‘balanced’, adds weight to each class depending on the class balance
+\item fit\_intercept = False, bias added to the decision function
+\end{itemize}
 
 \section{Conclusion and Future Works}
-\label{Conclusion+FutureWorks} In this work, we applied classification algorithms to the task of diagnosing Parkinson's Disease using handwriting samples.
-Our dataset was relatively small in size, a problem we hope to address in the future through development of a web portal.
-Along with our models, we devised a handwriting assessment based on precedents in this research area as well as data available to us.
-Once this portal is complete, we hope to perform clinical studies with our partners from Penn State University to evaluate the handwriting assessment and develop data considering temporal stages of Parkinson’s Disease-by analyzing handwriting images from early and later stages of Parkinson’s.
+\label{Conclusion+FutureWorks} 
+In this work, we applied classification algorithms to the problem of early diagnosis of Parkinson's Disease using handwriting samples.
+Our dataset was relatively small in size, a problem we hope to address in the future by gathering data through our web portal.
+Along with our models, we devised a handwriting assessment based on precedents open-source datasets in this research area.
+View the assessment in Appendix \ref{app:assessment}.
+Once the web portal is complete, we hope to perform clinical studies with our partners from Penn State University.
+In these studies, we will evaluate the handwriting assessment and develop a handwriting dataset that considers temporal stages of Parkinson’s disease by analyzing handwriting samples from early and later stages of PD.
 
 Furthermore, we hope to increase the accessibility of our handwriting assessment through online availability using a touch-screen device, such as a phone or tablet.
-This enables us to take advantage of signals provided by such a device.
-A similar exercise may be performed using keystroke data from a computer and asking a patient to type, rather than draw.
-The next iteration of this work aspires to further improve model performance and work toward automatic and real-time detection of Parkinson’s disease.
+This enables us to take advantage of device signals.
+A similar exercise, with typing instead of drawing, may be performed using keystroke data from a computer.
+
+The next iteration of this work aspires to design a Convolutional Neural Network (CNN) deep learning model.
+View details about image preprocessing in Appendix \ref{app:imgextraction}.
+We hope the CNN will further improve prediction accuracy and work toward automatic and real-time detection of Parkinson’s disease.
+% \red{it is better to add more references as they are not unlimited.}
 
@@
 \clearpage
+
+\appendix
+
+% Appendix A
+% Figure 2 - Feature Extraction Procedure
+\section{Image Feature Extraction Procedure}
+\label{app:imgextraction}
+
+To develop useful image features that can serve as input to a Convolutional Neural Network (CNN) model, we extracted the exam trace (ET), the outline for the patient to replicate, and the handwriting trace (HT), the outline the patient drew, from all our images.
+To do so, we followed the process below.
+
+Exam Trace:
+
+\begin{enumerate}
+\item Mean Blur (5 x 5 kernel)
+\item Binary Threshold
+
+Consider I to represent a pixel in an image with three color channels: red, green, and blue, written as I(r), I(g), and I(b)
+
+\[I((r, g, b)) = \begin{cases} 
+    0 & \text{if } I(r) < 90 \land I(g) < 90 \land I(b) < 90 \\
+    1 & \text{otherwise}
+\end{cases}\]
+
+\item Dilate (4 x 4 kernel)
+\end{enumerate}
+
+\begin{figure}[h] 
+\label{fig: fig2}
+\centering 
+\includegraphics[scale = 0.175]{images/exam_trace.png}
+\caption{Exam Trace Extraction Process}
+\end{figure}
+
+\vfill\null
+\columnbreak
+
+Handwriting Trace:
+
+\begin{enumerate}
+\item Median Blur (5 x 5 kernel)
+\item Binary Threshold
+
+Consider I to represent a pixel in an image with three color channels: red, green, and blue, written as I(r), I(g), and I(b)
+
+\[I((r, g, b)) = \begin{cases} 
+    0 & \text{if } I(r) < 200 \land I(g) < 200 \land I(b) < 200 \\
+    1 & \text{otherwise}
+\end{cases}\]
+
+\item Difference Image (with extracted ET)
+\item Invert and Dilate Image
+\end{enumerate}
+
+\begin{figure}[h] 
+\label{fig: fig3}
+\centering 
+\includegraphics[scale = 0.22]{images/hd_trace.png}
+\caption{Handwriting Trace Extraction Process}
+\end{figure}
+
+\clearpage
+
+Next, we combined the extracted exam trace and handwriting trace, producing an image with minimal features that has the potential to form a strong CNN model.
+
+\begin{figure} [h]
+\label{fig:fig4}
+\centering 
+\includegraphics[scale = 0.26]{images/combination.png}
+\caption{Blending HT and ET to Form the Final Image}
+\end{figure}
+
+\clearpage
+
+% Appendix B
+\section{Handwriting Assessment}
+\label{app:assessment}
+
+\begin{figure} [h]
+\label{fig:fig5}
+\centering 
+\includegraphics[scale = 0.4]{images/hand_assess.png}
+\caption{Handwriting Assessment Developed for the Web Portal}
+\end{figure}
+
+\clearpage
+
+% Appendix C
+\section{Pictures and Use Cases of PD Diagnosis Web Portal Interface}
+
+There are two use cases of the web portal: submitting handwriting assessments and viewing assessment history. They are pictured below. The process of performing these actions is as follows:
+
+Submitting Handwriting Assessments
+
+\begin{enumerate}
+\item The user logs into their account on the portal (or creates an account if she does not have one) and navigates to the “Submit A Test” page.
+\item The user prints out the handwriting assessment .pdf available on the page.
+\item 
+The user fills out the exam, scans it, and uploads a photo to the page.
+\item After a few moments, the user receives a PD diagnosis, with their \% chance of having PD. The exam and its results are saved in the “Exam History” page.
+\end{enumerate}
+
+\begin{figure}[h]
+\label{fig:fig6}
+\centering 
+\includegraphics[scale = 0.3]{images/Submit_Test.png}
+\caption{"Submit A Test" page UI}
+\end{figure}
+
+\vfill\eject
+
+Viewing Assessment History
+
+\begin{enumerate}
+\item The user logs into their account on the portal and navigates to the “Exam History” page.
+\item The user can now view information about all their past exams, including the date, a picture of their assessment, age and gender information submitted alongside the assessment, and results.
+\item The user views their previous assessment submissions by clicking on the exam icons available next to each exam number on the page.
+\end{enumerate}
+
+\begin{figure} [h]
+\label{fig: fig7}
+\centering 
+\includegraphics[scale = 0.3]{images/Exam_Hist.png}
+\caption{"Exam History" page UI}
+\end{figure}
+
+\clearpage
+
 \end{document}

### 2021-09-14 Submission/Paper/Paper.tex
submitting paper :pray:

@@
  % Remove the next line if you don't require it.
+\usepackage{url}
+\usepackage{breakurl}
+\usepackage[breaklinks]{hyperref}
+\def\UrlBreaks{\do\/\do-}
 
@@
 Parkinson’s disease (PD) is debilitating, progressive, and clinically marked by motor symptoms.
-As the second most common neurodegenerative disease and with no approved treatments, it affects over 10 million lives around the world.
-Existing diagnoses methods have limitations, such as the expense of visiting doctors and the challenge of automated early detection, considering that behavioral differences in patients and healthy individuals are often indistinguishable in early stages.
-Micrographia is a disorder commonly observed in early stages of PD.
-In order to establish mechanisms for early detection of PD, we applied machine learning techniques to extract signs of micrographia from drawing samples gathered from two open-source datasets, achieving a predictive accuracy of 94\%.
-This work also sets the foundations for a publicly available and user-friendly web portal that anyone with access to a pen, printer, and phone can use for early detection of PD.
+As the second most common neurodegenerative disease in the world, it affects over 10 million lives globally.
+Existing diagnoses methods have limitations, such as the expense of visiting doctors and the challenge of automated early detection, considering that behavioral differences in patients and healthy individuals are often indistinguishable in the early stages.
+However, micrographia, a handwriting disorder that leads to abnormally small handwriting, tremors, dystonia, and slow movement in the hands and fingers, is commonly observed in the early stages of PD.
+In this work, we apply machine learning techniques to extract signs of micrographia from drawing samples gathered from two open-source datasets and achieve a predictive accuracy of 94\%.
+This work also sets the foundations for a publicly available and user-friendly web portal that anyone with access to a pen, printer, and phone can use for early PD detection.
 \end{abstract}
@@
 Parkinson’s disease (PD) is a neurodegenerative, chronic, and progressive nervous system disorder that affects movement.
-More than 10 million people worldwide are currently living with PD, and the number of cases is expected to more than double in the next decade.
+PD affects more than 10 million people worldwide, and this number is expected to double by 2030.
 \citep{choi2017refining} Symptoms include tremors, slowness of movement, stiffness, and changes in writing skills.
@@
 
-Parkinson's Disease cannot be treated, although specific drugs and medications can assist with symptoms in early stages, potentially preventing the disease’s progression to more severe stages.
+Parkinson's disease cannot be treated, although specific drugs and medications can assist with early-stage symptoms, potentially preventing the progression to more severe stages.
 Early detection and prognosis of PD are crucial for assisting patients to retain a good quality of life.
-However, diagnosing Parkinson’s disease in its early stages is a very challenging task, and there are currently no specific tests designed to diagnose PD \citep{national_institute_of_neurological_disorders_and_stroke}.
+However, diagnosing Parkinson’s disease in its early stages is a very challenging task, and there are currently no specific tests designed or approved to diagnose PD \citep{national_institute_of_neurological_disorders_and_stroke}.
 Diagnosis is based on a thorough examination performed by a trained medical official, including a neurological examination, medical history evaluation, blood and laboratory tests, and brain scans.
-Even with these procedures, PD is misdiagnosed up to 30\% of the time, especially in early stages, due to the many Parkinson’s mimics, the main ones being Essential Tremors and Drug Induced Parkinson’s.
+Even with these procedures, PD is misdiagnosed up to 30\% of the time because of the many PD mimics, such as Essential Tremors and Drug-Induced Parkinson’s.
 Additionally, up to 20\% of PD patients are undiagnosed \citep{schrag_ben-shlomo_quinn_2002}.
-Receiving a PD diagnosis is expensive, time consuming, and non-accessible, as reported by 21\% of patients who had to visit their general provider thrice before receiving a specialist referral for their condition.
+Receiving a PD diagnosis is expensive, time-consuming, and non-accessible, as reported by 21\% of patients who had to visit their general provider thrice before receiving a specialist referral for their condition.
 \citep{gavidia_2020}
 
-Tools that can make the diagnosis process accurate, accessible, automatic, real-time, early, and free of cost can have tremendous impact for Parkinson’s patients.
-In this study, we apply machine learning strategies for PD prediction based upon the existing drawing samples resources of micrographia.
+Tools that make the diagnosis process accurate, accessible, automatic, real-time, early, and free of cost can have a tremendous impact on Parkinson’s patients.
+In this study, we apply machine learning strategies to predict PD based upon drawing samples that exhibit signs of micrographia.
 
@@
 \label{related-works}
-Prior works have incorporated the use of voice recordings, electroencephalogram (EEG) signals, and smart devices to create models that deduce whether a patient has PD or not.
-\citep{zhao2014automatic} hypothesized that patients with PD exhibit deficits in the production of emotional speech.
-To test this conjecture, five patients and seven healthy individuals were used to recognize Parkinson’s disease through voice recordings.
+Prior works have incorporated voice recordings, electroencephalogram (EEG) signals, and smart devices to create models that diagnose PD.
+\citet{zhao2014automatic} hypothesized that patients with PD exhibit deficits in the production of emotional speech.
+To test this conjecture, voice recordings from five patients and seven healthy individuals were used to detect Parkinson’s disease.
 Naive Bayes, Random Forests, and Support Vector Machines were applied for classification, achieving 65.5\% and 73.33\% accuracies on classifying PD and control.
-\citep{oh2020deep} utilized EEG signals and a Convolutional Neural Network (CNN) to detect PD by assessing whether the EEG signals depicted brain abnormalities, achieving 88.25\% accuracy.
-\citep{drotar2014analysis} employed the use of a digitizing tablet to assess both in-air and on-surface kinematic variables during handwriting of a sentence in 37 PD patients on medication and 38 age and gender-matched healthy controls.
+\citet{oh2020deep} utilized EEG signals and a Convolutional Neural Network (CNN) to detect PD by assessing whether the EEG signals depicted brain abnormalities, achieving 88.25\% accuracy.
+\citet{drotar2014analysis} employed the use of a digitizing tablet to assess both in-air and on-surface kinematic variables during handwriting of a sentence in 37 PD patients on medication and 38 age and gender-matched healthy controls.
 Using Support Vector Machines, an accuracy of 85.61\% was achieved.
-However, these studies require patients to visit a neurologist to access a smart device and undergo various scans like EEG and PET, making the process expensive, time-consuming, and difficult to access.
-In this study, we aim to make the PD diagnosis process more accurate, efficient, and accessible by using images of handwriting samples to automate the PD diagnosis process.
+
+These studies require patients to visit a neurologist to access a smart device and undergo various scans like EEG and PET, making the process expensive, time-consuming, and difficult to access.
+In this research, we aim to make the PD diagnosis more accurate, efficient, and accessible by using images of handwriting samples to automate the diagnosis process.
 
@@
 \paragraph{Dataset}
-\label{sec:Dataset} Our dataset was formed by combining the New HandPD and Old HandPD dataset \citep{pereira2016new}.
-It consisted of 158 individuals, 53 healthy and 105 PD patients.
-Each patient drew 8 images, 4 spirals and 4 meander.
-With these images, we constructed 2 datasets, one consisting of extracted numerical features and the other consisting of images.
-The process of assembling the image dataset and its uses are discussed further in Appendix ....
+\label{sec:Dataset} We formed our dataset by combining the New HandPD and Old HandPD dataset \citep{pereira2016new}.
+It consisted of 158 individuals, split into 53 healthy individuals and 105 PD patients.
+Each patient drew 8 images: 4 spirals and 4 meanders.
+With these images, we constructed 2 datasets, one with extracted numerical features and the other with images.
+The process of assembling the image dataset and its uses are discussed further in Appendix A.
 
@@
 \label{sec:Preprocessing} 
-We mimicked the feature extraction process used \citep{pereira2016new} to extract 9 numerical features from the images.
-First, the handwritten trace (HT) and exam trace (ET) were extracted from the image.
-Figure (X) shows an example image and the extracted HT and ET.
-Using the HT and ET, the below features were computed:
+We mimicked the feature extraction process used by \citep{pereira2016new} to extract 9 numerical features from the images.
+First, we extracted the handwritten trace (HT) and exam trace (ET) were extracted from each image.
+The HT is the outline the patient drew and the ET is the outline the patient tried to replicate.
+Appendix \ref{app:webportal} show images of the extracted HT and ET.
+Using the traces, the below features were computed:
 
@@
 % \red{it is better to show some notation first or explain the notation after each formula. Otherwise, the reviewers will get confused.} 
-\item The root mean square (RMS) of the differences between the HT and ET radii.
-The radius of the HT or ET can be defined as the length of the straight line that connects an arbitrary point to the center of the HT or ET and is shown in figure (X).
+\item[F1:] The root mean square (RMS) of the differences between the HT and ET radii.
+The radius of the HT or ET can be defined as the length of the straight line that connects an arbitrary point to the center of the HT or ET.
 \[RMS = \sqrt{\frac{1}{N} * \sum_\SUP{i=1}^N(r_\SUP{HT}^i - r_\SUP{ET}^i)^2}\]
 
-$N$ is the number of sample points on the HT and ET, and $r_\SUP{HT}^i$ + $r_\SUP{ET}^i$ denote the HT and ET radii for the $i$th point.
+$N$ is the number of sample points on the HT and ET, and $r_\SUP{HT}^i$ and $r_\SUP{ET}^i$ denote the HT and ET radii for the $i$th point.
 
-\item The maximum difference between the HT and ET radii. 
+\item[F2:] The maximum difference between the HT and ET radii. 
 \[\Delta max = max(|r_\SUP{HT}^i - r_\SUP{ET}^i|)\]
@@
 % \red{you may want to remove F3, F4, etc below}
-\item F3: The minimum difference between the HT and ET radii. 
+\item[F3:] The minimum difference between the HT and ET radii. 
 \[\Delta min = min(|r_\SUP{HT}^i - r_\SUP{ET}^i|)\]
 
-\item F4: The standard deviation of the differences between the HT and ET radii. 
+\item[F4:] The standard deviation of the differences between the HT and ET radii. 
 \[s = \sqrt{\frac{1}{N-1}\sum_{i=1}^N(r_\SUP{HT}^i - r_\SUP{ET}^i)^2}\]
 
-\item F5: The Mean Relative Tremor (MRT) of a given individual’s HT.
+\item[F5:] The Mean Relative Tremor (MRT) of a given individual’s HT.
 This is defined as the mean difference between the radius of a given sample and its D left-nearest neighbors.
@@
 Figures 6-8 are computed utilizing the equation for relative tremor: $|r_\SUP{ET}^i - r_\SUP{HT}^\SUP{i-D+1}|$
-\item F6: Maximum ET
-\item F7: Minimum ET
-\item F8: Standard Deviation of ET values
-\item F9: The number of times the difference between HT and ET radii changes from positive to negative.
+\item[F6:] Maximum ET
+\item[F7:] Minimum ET
+\item[F8:] Standard Deviation of ET values
+\item[F9:] The number of times the difference between HT and ET radii changes from positive to negative.
 \end{enumerate}
@@
 
-Additionally, we noticed there was a large class-imbalance present in our dataset, with 53 healthy and 105 PD patients.
-After performing experiments with our machine learning models, we discovered that this imbalance led to overfitting and undesirable accuracies, even after the assignation of higher weight to the healthy class.
-To cope with this, we truncated our original dataset by removing the 31 PD patients from the New HandPD dataset.
-This resulted in 127 patients, 53 healthy and 74 PD, which greatly boosted our results.
-The final dataset of 158 patients was randomly split between train (76.5\%), validation (8.5\%) and hold-out test (15\%) sets.
-Table \ref{tab:table1} shows our demographics for cohort of patients.
+Two other features we include in our predictions are a patient's gender and age, considering that Parkinson's disease mainly impacts individuals above age 50 and is 1.5 times more common in males \citep{reekes2020sex}.
+
+Additionally, we noticed there was a large class imbalance in our dataset, with 53 healthy and 105 PD patients.
+After performing experiments with our machine learning models, we discovered that this imbalance led to overfitting and undesirable performances, even after weighting the classes.
+To cope with this, we truncated our original dataset by removing the 31 PD patients from the New HandPD dataset, which greatly boosted our model's ability to learn useful patterns.
+Our final dataset of 127 patients, 53 healthy and 74 PD, was randomly split between train (76.5\%), validation (8.5\%), and hold-out test (15\%) sets.
+Table \ref{tab:table1} shows the demographics for our cohort of individuals.
 
@@
 \label{sec:SVM}  
-\paragraph{(1) Support Vector Machines on Numerical Features Dataset} In model 1, we utilized a Support Vector Machine (SVM) \citep{708428} where the PD diagnosis label was analyzed on the nine extracted numerical features.
-We used 10-fold Cross-Validation (CV) \citep{stone1974cross} on the held-out validation set to maximize accuracy by choosing an optimal kernel (Radial Base, Linear, or Polynomial), class weight (None or Balanced), probability threshold and lambda.
-After training and validating the model on the image level, we tested it on the patient-level, extracting all 8 images from 11 PD and 8 healthy patients (15\% test set) and selecting an optimal aggregation scheme for patient-level predictions.
+\paragraph{(1) Support Vector Machines} In model 1, we utilized a Support Vector Machine (SVM) \citep{708428} to diagnose PD given the nine extracted numerical features, age, and gender.
+We used 10-fold Cross-Validation (CV) \citep{stone1974cross} on the validation set to maximize accuracy by choosing an optimal kernel (Radial Base, Linear, or Polynomial), class weight (None or Balanced), probability threshold, and lambda.
+After training and validating the model on the image level, we tested it on the patient level, extracting all 8 images from 11 PD and 8 healthy patients (15\% test set) and selecting an optimal aggregation scheme for patient-level predictions.
 
 \label{sec:LogReg}  
-\paragraph{(2) Regularized Logistic Regression on Numerical Features Dataset} In model 2, we employed Regularized Logistic Regression \citep{tibshirani1996regression} strategies, regressing the PD diagnosis label against the nine extracted numerical features.
+\paragraph{(2) Regularized Logistic Regression} In model 2, we employed Regularized Logistic Regression \citep{tibshirani1996regression} strategies, regressing the PD diagnosis label against the nine extracted numerical features, age, and gender.
 With 10-fold CV, we iterated over different lambda values, probability thresholds, and loss and solver functions to maximize accuracy for our image-level predictions.
-After training and validating the model on the image level, we tested it on the patient-level, extracting all 8 images from 5 PD and 4 healthy patients (15\% test set) and selecting an optimal aggregation scheme for patient-level predictions.
+We tested the model on the patient level, extracting all 8 images from 11 PD and 8 healthy patients (15\% test set) and determining an optimal aggregation scheme for patient-level predictions.
 
@@
 \label{Results} To maximize the performance of both models, we utilized a probability threshold.
-First, we trained, validated, and tested the models on the image-level.
-All performance metrics in Table \ref{tab:table2} are based on image-level class assignments.
+First, we trained, validated, and tested the models on the image level.
+All performance metrics in Table \ref{tab:table2} are based on image level class assignments from the held-out test set.
 
 However, our web portal will consider 6 - 8 different drawings per patient in the diagnosis process.
-To mimic this functionality, we tested each model on the patient-level with an aggregation scheme.
+To mimic this functionality, we tested each model on the patient level with an aggregation scheme.
 We chose an optimal scheme from three options: applying a PD label to a patient if the model diagnosed 2/8 images as signs of PD, if the averaged probability score from all 8 images was greater than 0.5, or if the model predicted more than half the images to belong to a PD patient.
-The last scheme performed best, likely because the model tended to predict only a few images incorrectly per patient.
+The last scheme performed best because the model mainly predicted only a few outlier images incorrectly (if any images were predicted wrong) per patient.
 
 Both models received the same patient-level accuracy: 0.9444.
-Additionally, we compared their Receiver Operating Characteristic (ROC) curves (Figure \ref{fig:fig1}) when tested on 10 different random selections of 19 patients (11 PD and 8 Control).
-Both models performed similarly on each test set, although Regularized Logistic Regression was more consistent because of the regularization applied.
+Additionally, we compared their Receiver Operating Characteristic (ROC) curves (Figure \ref{fig:fig1}) when tested on 10 random selections of 19 patients (11 PD and 8 Control).
+Both models performed similarly on each test set, although Regularized Logistic Regression was more consistent.
+Optimal hyperparameters for each model are listed below.
 
-The best hyperparameters for the SVM model were:
+Support Vector Machines:
 \begin{itemize}
@@
 
-The best hyperparameters for the Regularized Logistic Regression model were:
+Regularized Logistic Regression:
 \begin{itemize}
@@
 \label{Conclusion+FutureWorks} 
-In this work, we applied classification algorithms to the problem of early diagnosis of Parkinson's Disease using handwriting samples.
-Our dataset was relatively small in size, a problem we hope to address in the future by gathering data through our web portal.
-Along with our models, we devised a handwriting assessment based on precedents open-source datasets in this research area.
-View the assessment in Appendix \ref{app:assessment}.
+In this work, we applied classification algorithms to handwriting samples to diagnose Parkinson's disease in its early stages.
+Our dataset was relatively small in size, which we will address in the future by gathering data through our web portal.
+Our mockups and plans for the website are detailed in Appendix \ref{app:webportal}.
+Additionally, we devised a handwriting assessment based on precedents and open-source datasets in this research area, which is available in Appendix \ref{app:assessment}.
 Once the web portal is complete, we hope to perform clinical studies with our partners from Penn State University.
-In these studies, we will evaluate the handwriting assessment and develop a handwriting dataset that considers temporal stages of Parkinson’s disease by analyzing handwriting samples from early and later stages of PD.
+In these studies, we will evaluate the handwriting assessment and develop a handwriting dataset that considers temporal stages of Parkinson’s disease by analyzing handwriting and drawing samples from different stages of PD.
 
-Furthermore, we hope to increase the accessibility of our handwriting assessment through online availability using a touch-screen device, such as a phone or tablet.
-This enables us to take advantage of device signals.
-A similar exercise, with typing instead of drawing, may be performed using keystroke data from a computer.
+After completing the web portal, we hope to boost the accessibility of our handwriting assessment through online deployment.
+Ideally, a patient with a touch-screen device, such as a phone or tablet, will be able to take a quick, easy, online assessment.
+This also enables us to take advantage of device signals.
+A similar exercise, with typing instead of drawing, can be performed using keystroke data from a computer.
 
-The next iteration of this work aspires to design a Convolutional Neural Network (CNN) deep learning model.
-View details about image preprocessing in Appendix \ref{app:imgextraction}.
-We hope the CNN will further improve prediction accuracy and work toward automatic and real-time detection of Parkinson’s disease.
+The next iteration of our work with machine learning and deep learning models will be to design a Convolutional Neural Network (CNN) for analysis of the drawing images.
+We have already designed the feature extraction process, pictured in Appendix \ref{app:imgextraction}.
+The CNN will further improve prediction accuracy and work toward automatic and real-time detection of Parkinson’s disease.
 % \red{it is better to add more references as they are not unlimited.}
@@
 % References
+
 \bibliography{jmlr-sample}
+\UrlBreaks
 \nocite{*}
+\justifying
+
+\clearpage
+\appendix
+
+% Appendix B
+\section{Pictures and Use Cases of PD Diagnosis Web Portal Interface}
+\label{app:webportal}
+
+There are two use cases of the web portal: submitting handwriting assessments and viewing assessment history. The process to perform these actions is detailed below.
+
+Submitting Handwriting Assessments
+
+\begin{enumerate}
+\item The user logs into their account on the portal (or creates an account if she does not have one) and navigates to the “Submit A Test” page.
+\item The user prints out the handwriting assessment .pdf available on the page.
+\item 
+The user fills out the exam, scans it, and uploads a photo to the page.
+\item After a few moments, the user receives a PD diagnosis, with their \% chance of having PD. The exam and its results are saved in the “Exam History” page.
+\end{enumerate}
+
+\begin{figure}[h]
+\label{fig:fig6}
+\centering 
+\includegraphics[scale = 0.3]{images/Submit_Test.png}
+\caption{"Submit A Test" page UI}
+\end{figure}
+
+\vfill\eject
+
+Viewing Assessment History
+
+\begin{enumerate}
+\item The user logs into their account on the portal and navigates to the “Exam History” page.
+\item The user can now view information about all their past exams, including the date, a picture of their assessment, age and gender information submitted alongside the assessment, and results.
+\item The user views their previous assessment submissions by clicking on the exam icons available next to each exam number on the page.
+\end{enumerate}
+
+\begin{figure} [h]
+\label{fig:fig7}
+\centering 
+\includegraphics[scale = 0.3]{images/Exam_Hist.png}
+\caption{"Exam History" page UI}
+\end{figure}
 
@@
 
-\appendix
+% Appendix B
+\section{Handwriting Assessment}
+\label{app:assessment}
+
+\begin{figure} [h]
+\label{fig:fig5}
+\centering 
+\includegraphics[scale = 0.4]{images/hand_assess.png}
+\caption{Handwriting Assessment Developed for the Web Portal}
+\end{figure}
+
+\clearpage
 
@@
 
-To develop useful image features that can serve as input to a Convolutional Neural Network (CNN) model, we extracted the exam trace (ET), the outline for the patient to replicate, and the handwriting trace (HT), the outline the patient drew, from all our images.
+To develop useful image features to input into a Convolutional Neural Network (CNN) model, we extracted an exam trace (ET) and a handwriting trace (HT) from all our images and combined them.
 To do so, we followed the process below.
@@
 
-Consider I to represent a pixel in an image with three color channels: red, green, and blue, written as I(r), I(g), and I(b)
+I represents each pixel (x, y) in an image, with three color channels: red, green, and blue, written as I(r), I(g), and I(b)
 
@@
 \centering 
-\includegraphics[scale = 0.175]{images/exam_trace.png}
+\includegraphics[scale = 0.18]{images/exam_trace.png}
 \caption{Exam Trace Extraction Process}
@@
 
-\clearpage
-
-% Appendix B
-\section{Handwriting Assessment}
-\label{app:assessment}
-
-\begin{figure} [h]
-\label{fig:fig5}
-\centering 
-\includegraphics[scale = 0.4]{images/hand_assess.png}
-\caption{Handwriting Assessment Developed for the Web Portal}
-\end{figure}
-
-\clearpage
-
-% Appendix C
-\section{Pictures and Use Cases of PD Diagnosis Web Portal Interface}
-
-There are two use cases of the web portal: submitting handwriting assessments and viewing assessment history. They are pictured below. The process of performing these actions is as follows:
-
-Submitting Handwriting Assessments
-
-\begin{enumerate}
-\item The user logs into their account on the portal (or creates an account if she does not have one) and navigates to the “Submit A Test” page.
-\item The user prints out the handwriting assessment .pdf available on the page.
-\item 
-The user fills out the exam, scans it, and uploads a photo to the page.
-\item After a few moments, the user receives a PD diagnosis, with their \% chance of having PD. The exam and its results are saved in the “Exam History” page.
-\end{enumerate}
-
-\begin{figure}[h]
-\label{fig:fig6}
-\centering 
-\includegraphics[scale = 0.3]{images/Submit_Test.png}
-\caption{"Submit A Test" page UI}
-\end{figure}
-
-\vfill\eject
-
-Viewing Assessment History
-
-\begin{enumerate}
-\item The user logs into their account on the portal and navigates to the “Exam History” page.
-\item The user can now view information about all their past exams, including the date, a picture of their assessment, age and gender information submitted alongside the assessment, and results.
-\item The user views their previous assessment submissions by clicking on the exam icons available next to each exam number on the page.
-\end{enumerate}
-
-\begin{figure} [h]
-\label{fig: fig7}
-\centering 
-\includegraphics[scale = 0.3]{images/Exam_Hist.png}
-\caption{"Exam History" page UI}
-\end{figure}
-
-\clearpage
-
 \end{document}

### 2021-11-24 Submission/Paper/Paper.tex
uploading paper to arXiv

@@
  %\documentclass[tablecaption=bottom]{jmlr}% journal article
- \documentclass[pmlr,twocolumn,10pt]{jmlr} % W&CP article
+ \documentclass[pmlr,twocolumn,10pt,breaklinks, x11names,table]{jmlr} % W&CP article
 
@@
 \usepackage{breakurl}
-\usepackage[breaklinks]{hyperref}
+\usepackage{ragged2e}
+% \usepackage[breaklinks]{hyperref}
 \def\UrlBreaks{\do\/\do-}
@@
 
-\usepackage[table]{xcolor}
+% \usepackage[table]{xcolor}
 \newcommand\red[1]{{\color{red}#1}}
@@
  % change the arguments, as appropriate, in the following:
-\jmlrvolume{LEAVE UNSET}
+\jmlrvolume{ML4H Extended Abstract Arxiv Index}
 \jmlryear{2021}
-\jmlrsubmitted{LEAVE UNSET}
-\jmlrpublished{LEAVE UNSET}
+\jmlrsubmitted{2021}
+\jmlrpublished{}
 \jmlrworkshop{Machine Learning for Health (ML4H) 2021} % W&CP title
@@
 % Authors with different addresses and equal first authors:
-% \author{Riya Tyagi \nametag{\thanks{Authors contributed equally}},
-% Tanish Tyagi \nametag{\footnotemark[1]}, 
-% Ming Wang,
-% Lijun Zhang
-% \centering \Email{ 
-% \\[\bigskipamount]  
-% rtyagi@exeter.edu, ttyagi@mgh.harvard.edu, mwang@phs.psu.edu, lzhang6@pennstathealth.psu.edu}
-% }
+\author{Riya Tyagi \nametag{\thanks{Authors contributed equally}},
+Tanish Tyagi \nametag{\footnotemark[1]}, 
+Ming Wang,
+Lijun Zhang
+\centering \Email{ 
+\\[\bigskipamount]  
+rtyagi@exeter.edu, ttyagi@mgh.harvard.edu, mwang@phs.psu.edu, lzhang6@pennstathealth.psu.edu}
+}
 
@@
 
-    \subfloat{{\includegraphics[scale = 0.55]{images/logreg_roc.png} }}%
-    \subfloat{\includegraphics[scale = 0.55]{images/svm_roc.png}} %
+    {{\includegraphics[scale = 0.55]{images/logreg_roc.png} }}%
+    {\includegraphics[scale = 0.55]{images/svm_roc.png}} %
 
 \end{figure*}
-
 \section{Methods}
@@
 Additionally, we devised a handwriting assessment based on precedents and open-source datasets in this research area, which is available in Appendix \ref{app:assessment}.
+We strive to boost the accessibility of our handwriting assessment by online deployment through a web portal.
+Ideally, a patient with a touch-screen device will be able to take a quick, easy, online assessment.
 Once the web portal is complete, we hope to perform clinical studies with our partners from Penn State University.
 In these studies, we will evaluate the handwriting assessment and develop a handwriting dataset that considers temporal stages of Parkinson’s disease by analyzing handwriting and drawing samples from different stages of PD.
-
-After completing the web portal, we hope to boost the accessibility of our handwriting assessment through online deployment.
-Ideally, a patient with a touch-screen device, such as a phone or tablet, will be able to take a quick, easy, online assessment.
-This also enables us to take advantage of device signals.
-A similar exercise, with typing instead of drawing, can be performed using keystroke data from a computer.
 
@@
 \bibliography{jmlr-sample}
-\UrlBreaks
+%\UrlBreaks
 \nocite{*}
-\justifying
+\justify{}
 
@@
 
-\vfill\null
-\columnbreak
+\vfill\eject
+% \columnbreak
 
